### 2015-04-12 glsb.tex
initial commit

\documentclass[12pt,preprint]{aastex}
%\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

\shorttitle{Short Title}
\shortauthors{Yoachim et al.}

\begin{document}

\title{Giant Low Surface Brightness Galaxies as Merger Remnants}

\author{Peter Yoachim\altaffilmark{1}, Denise Shmitz\altaffilmark{1}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{XXX-U Mich}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}

\begin{abstract}
We present IFU observations of the giant low surface brightness galaxies Malin~2 and UGC~6614.  We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.  We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone a high angular momentum merger which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.  We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.  The stellar populations of the GLSB disks are dominated by old metal-poor stars, while the central ellipticals are metal rich.

\end{abstract}
\keywords{galaxies: kinematics and dynamics --- galaxies: formation --- galaxies: structure}

\section{Introduction}

Since the discovery of Malin~1 \citep{Bothun87}, giant low surface brightness galaxies (GLSB) have presented a unique problem for galaxy formation theories.  Low surface brightness (LSB) galaxies are typically defined as disks with central surface brightnesses fainter than 23 $B$ mag arcsec$^2$.  These disks are incredibly large, with Malin~1 being detected to a radius of over 100 kpc \citep{Moore06}.  It is difficult to imagine how a stellar disk could form within a merger-driven $\Lambda$CDM cosmology.

A wide variety of formation scenarios have been proposed for GLSB systems.  \citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies xxx-expand this a bit.

Meanwhile, observers tend to classify GLSB systems as normal spirals.  \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.  Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.

XXX-add discussion of possibility the centers of GLSBs are normal galaxies.

In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.

The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.  The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum. xxx-this goes in the discussion I think. \citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.

GLSBs are typically classified as spriral galaxies \citep{Das13}, however, high resolution imaging of Malin~1 has shown that the central region appears to be a normal

\citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.  Lots of good stuff on fast/slow rotators.  Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.  They don't see any sharp transition like I do, all very smooth age and metal curves.

\citet{Kasparova14} has an amazing analysis of Malin 2.  They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.  They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.  They think the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.  I think this is begging the question a little bit

\citet{Pickering97} has the \HI\ rotation curves of these guys.  For UGC 6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.  And $3.6 \pm 0.4 \times 10^{10} \msun h_{75}^{-2}$for Malin 2.  Notes that these are galaxies that are massive and DM dominated.  In Malin 2, they find some gas moving relative to the regular rotating disk, and suspect that a dwarf fell though and stimulated star formation and this could be how stars managed to form in the low density environment.

Can we say that the stars formed in a higher density environment and then got dispersed.

\citet{Das13} look at the environments of GLSB systems.  He says that GLSBs are an extreme form of late type spiral galaxies.  I think I can show that no, they are really normal elliptical galaxies that happen to have accreted disks.

Standard catalogs list these systems as Sd and Sa galaxies, so they are commonly thought of as spirals.

Nice paper on galaxies that live in voids and how one did manage to build a polar \HI\ disk with no stars: \citet{Stanonik09}

Chemical abundances in a polar disk:  \citet{Spavone10}

a near scoop by \citet{Lelli10}.  They re-analyze \HI\ data on Malin 1 and one other.  But a nice place to look for introduction material.  They point out that GLSB galaxies might be normal HSB galaxies in the center.  They claim to see steeply rising rotation curves, and compare to formation mechanisms.

\citet{Morganti97} look at an elliptical with an \HI\ disk.  Find a nice flat rotation curve.
\citet{Emonts08}  Another massive \HI\ ring around an S0 galaxy.
\citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.

\citet{Barth07} analyze HST imaging of Malin 1 and find that the central object is well described as a normal SB0/a galaxy.  Makes good point that lots of the other large disk observations look like they are extensions of the inner galaxy, while Malin 1's disk is probably a distinct component.

\citet{Pen06} look at forming extended disks by disrupting a dwarf galaxy.

\citet{Ibata05} look at extended disk of M31.

\citet{Ibata13} claim M31 satellites are co-planer.

\citet{McConnachie09} M31 survey showing lots of merger structure.

Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html

another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm

From \citet{Matthews01b}, \HI\ measurements on the gals:
%name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
%F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
%UGC 6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.  I'll need to compare my stellar kinematics to the \HI\ kinematics.

\cite{Rahman2007} has Spitzer observations of a few GLSB galaxies.

\citet{Das10} find CO in Malin 2.  Make some points about it being stable

\citet{Mapelli12} making ring galaxies from off center collisions.

\citet{Mapelli08} look at if ring galaxies could evolve into GLSB systems.

\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.

\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.

\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.  They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.

\citet{Schweizer89} Do a similar study with IC 2006, where they observe an \HI\ ring around the elliptical galaxy to get the total mass at large radii.  Looks like they get out to about 12.5 kpc.

\citet{Oosterloo07} HIPASS detection of \HI\ gas around 30 early-type galaxies.  Most have regular disk or ring kinematics.  Suggest these are ancient.  They don't seem to have the resolution to do in-depth kinematics and DM halo stuff.

\citet{Magain13} look at strong lenses around 25 ellipticals, and then claim they see no evidence for extended DM halos.  Confusing plot--Maybe they get out to 5 $R_{1/2}$?  They say they only need a factor of 2, that could come from baryonic dark matter.

\citet{Spray95} CCD imaging of 8 GLSB systems.

\citet{Morganti13} Do modeling of ellipticals with declining velocity dispersion profiles.  Good place to start looking for the best way to model the long-slit data.

\citet{Buote12} review of dark matter in ellipticals from x-ray observations.

XXX-clearly need to look up bulge-to-disk metallicity gradient.  Lauren did it with colors in \citet{MacArthur04}.  Nice look with metallicity gradients as a function of scale-length, and kpc, and vrot and galaxy type.  Did spectra gradients in \citet{MacArthur09}.  MANGA would make this easy to compare...Maybe there's a SAURON paper on metallicity gradients.

XXX-need to look up some Thilker papers on extended UV disks, since these objects could be similar.  From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).  UGC 3642, GALEX shows a disk, and \HI\ is counter rotating.

\citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.  They think the gas and star formation is comming from minor mergers or accretion.

\citet{Salim12} Finds 2 more GLSB type objects -- could be a sign that there are multiple routes to making GLSB systems.

\begin{deluxetable}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$} & Stellar Mass & \colhead{\HI\ mass}\\
     &  \colhead{(DR 9)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms}  &\colhead{log$_{10}$M$_{\odot}$}&\colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  & 11.15 & 10.6\\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 & 10.66 & 10.5
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS.}
\end{deluxetable}

% Updating the Pickering MI masses:
% M_\HI\ = 2.36e5 * D^2 * int(S)
% D = c(z+0.5(1.0-q_0)z^2)/H_0
% int(S) = 4.4 Jy km/s for Malin 2
%        = 15.0 for UGC 6614
% cosmolopy using h = 0.704.  
% cosmolopy says D_L = 202.9 and 90.9 Mpc
% so that gives me M_\HI\'s of 4.27e10 and 2.92e10

%  using scales of 0.940 and 0.444 kpc/arcsec.

\begin{deluxetable}{l c c }
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Fitted Structural Properties}
\tablehead{
\colhead{Name} & \colhead{$h_r$}   &  \colhead{inclination}    \\
     &  \colhead{(arcsec)}   & \colhead{(deg)}      
\label{fitted_params}}    
\startdata
Malin 2 & 6.1 & 35.5  \\
UGC 06614 & 5.7 & 33.4
\enddata
\end{deluxetable}

The other way to measure the dark matter halo of an elliptical is to use gravitational lensing.  \citet{Belokurov07} find a large ring in SDSS.

%list of more lense papers here: http://www.galaxyzooforum.org/index.php?topic=275811.0

\section{Observations}

\subsection{IFU spectra}
We obtained spatially resolved spectroscopy of our target galaxies using the Mitchell Spectrograph (formerly VIRUS-P)\citep{Hill08} on the 2.7m Harlan J. Smith telescope at McDonald Observatory.  Observations were made during dark time in February, March, and April 2010.  Identical instrument setups were used for all observations.  The Mitchell Spectrograph with the VP-2 IFU bundle used here has a square array of 246 optical fibers which sample the 1.9\arcmin$\times$1.9\arcmin\ field-of-view with a 1/3 filling factor, with each fiber having a diameter of 4.23\arcsec.  The spectrograph images the spectrum of each fiber on a 2048$\times$2048 Fairchild Imaging CCD.

For each galaxy, observations were taken at three unique dither positions to provide nearly complete spatial coverage.  Individual science exposures were 30 minutes.  Malin 2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.  Observations of UGC 06614 had alignment issues between observing runs.  This resulted in a deep stack of 6 exposures, and a shallow stack with only 2 exposures.  With only 2 exposures, cosmic ray rejection becomes difficult, therefore, we use these shallow frames when looking at the surface brightness profiles, but use only the aligned deep co-add when analyzing the stellar kinematics and stellar populations. Twilight flat field frames, bias frames, and wavelength calibration Hg and Cd lamps were taken during the day.  Flux standard stars were observed in twilight.

%dates:  Feb 19, 20, 2010.  March 18-21, 2010.  April 6-8, 2010.

We use the Mitchell Spectrograph software pipeline Vaccine \citep{Adams2011} to perform basic reduction tasks.  Vaccine subtracts the over-scan region and generates and subtracts a bias frame.  Bad pixels are masked.  Twilight flats and arc lamps from each night are combined.  The combined flat frame is used to trace the spatial profile of each fiber and correct for pixel-to-pixel variation.  The combined arc lamp is used to fit a wavelength solution for each fiber.  We use a 4th order polynomial and find the wavelength solutions have a typical RMS of 0.06-0.2 \AA\ ($\sim0.1$ pixel).  Vaccine then masks potential cosmic rays and collapses each fiber to a one dimensional spectrum.  The fibers are adequately spaced, and our targets are predominately low surface brightness, so we find making a fiber cross-talk correction unnecessary.

Once the Vaccine routines are completed we make the following additional reductions using standard IRAF routines and custom IDL scripts.  The reduced twilight frames are used to generate a fiber-to-fiber flux correction (similar to a longslit illumination correction).  We use the b-spline procedure described in \citet{Kelson03} to generate background frames.  The corners of each frame contain enough empty fibers to measure the sky background in each exposure.  Because we bin fibers together, imperfect sky-subtraction represents a serious source of potential systematic errors.

The spectra are then rectified to a common wavelength scale, and the photo-spectroscopic standards are used to flux calibrate the spectra and correct for atmospheric extinction.  The spectra are then velocity shifted to the Local Standard of Rest.  Images taken at identical dither positions are averaged together with outlier rejection to eliminate any remaining cosmic rays.  Some observations were taken in non-photometric conditions, so before combining frames we scale them to a common average flux level.

Our final reduced data for each galaxy includes 738 spectra spanning a 1.9\arcmin$\times$1.9\arcmin\ field-of-view.  The spectra have a wavelength range of $\sim$3550-5840 with 2.2 \AA\ pixels (with some fibers only reaching 5500 \AA\ due to the warping of the trace).  The FWHM of reduced arc lamp images is 5.3 \AA, giving us a resolution of $R\sim700-1000$.  The fiber-to-fiber changes in resolution are less than 10\%.

With our final reduced data cubes, we used Penalized Pixel-Fitting (pPXF) \citep{Cappellari04} and Gas AND Absorption Line Fitting (GANDALF) \citep{Sarzi06} on each fiber to fit stellar velocities, stellar dispersions, and emission line velocities and fluxes.  For stellar templates we use a suite of SSP spectra from \citet{Bruzual03}.  We use GANDALF to measure the [\ion{O}{2}] doublet, [\ion{O}{3}] doublet, and the higher order Balmer lines \hb, H$\gamma$, H$\delta$, H$\epsilon$ while masking the night skyline at 5577 \AA.  The fit also includes a 4th degree multiplicative polynomial to correct for any dust or flux calibration mis-match between the observations and templates.  Because our data do not extend out to \ha, we cannot use the Balmer decrement to place tight constraints on the dust extinction.  While pPXF fits the stellar velocity dispersion, our instrumental resolution is low enough ($\sim140$ \kms) that we are unable to make meaningful velocity dispersion measurements beyond the central fibers.

In addition to individual fibers, we have binned neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers.

% Let's punt the APO spectra to the next paper--I don't think it adds much to this one anyway.
%\subsection{Longslit spectra}

%Observations were made using the Dual Imaging Spectrograph (DIS) on
%the ARC 3.5 meter telescope at Apache Point Observatory (APO).  Malin 2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.  Both galaxies were observed with the XXX gratings and multiple positions of the 1.5\arcsec\ slit.
%XXX-insert table with galaxy name, position, total exposure time
%XXX-insert figure showing slit positions overlayed on the SDSS thumbnails.

\section{Comparisons to Other Galaxies}

By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.  In the SDSS DR10 \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.  In this section, we compare the properties of the GLSB centers and disks with other systems.

\subsection{GLSB Centers}

Both our objects have been observed with SDSS, making it possible to compare them to a large number of systems.  The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.

To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddned $r$ magnitude between 13.5 and 17.7.  When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology selectors).  These are simply galaxies for comparison, not a rigorously defined volume-complete sample.  Our full SQL querries are shown in \S\ref{SQL}.  This gives us a sample of 141,001 objects, 45,703 of which have red colors.  Throughout, we use the CosmoloPy\footnote{\url{http://roban.github.com/CosmoloPy/}} fiducial cosmology ($h=0.704$, $\Omega_{m_0}=0.2726$, $\Omega_{\lambda_0}=0.7274$).

% based on WMAP7+BAO+H0 mean
%>>> fidcosmo
%{'tau': 0.087, 'omega_n_0': 0.0, 'sigma_8': 0.809, 'h': 0.704, 'N_nu': 0, 'omega_lambda_0': 0.7274, 'n': 0.963, 'Y_He': 0.24, 'z_reion': 10.4, 'omega_b_0': 0.0456, 'omega_k_0': 0.0, 't_0': 13.75, 'omega_M_0': 0.2726}
%xxx-clearly need to do a galfit to the central objects and show the residuals!  hmm, they are not well fit by simple Sersic profiles

Figure~\ref{elliptical_relations} shows where the GLSBs fall on the major galaxy relations.  We use extinction corrected magnitudes and $k$-corrected colors\citep{Chilingarian10}.  Both of our GLSBs lie on the red-sequence in a color-magnitude diagram.

The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the GLSBs are on the bright end of the red-sequence.

\begin{figure}
\epsscale{.4}
\plotone{Plots/Color_Magnitu_Diagram.eps}\plotone{Plots/Faber_Jackson_Relation.eps}\\
\plotone{Plots/Fundamental_Plane.eps}\plotone{Plots/mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin 2 and UGC 6614.  Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.  Left:  The $r$-band Fundamental Plane from SDSS along with our GLSB galaxies and best-fit line.  Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.   Looking at the SDSS data, our GLSB galaxies appear as normal red elliptical galaxies.  \label{elliptical_relations}}
\end{figure}

We follow \citet{Bernardi03,Bernardi03b} in fitting fundamental plane parameters to our selected SDSS galaxies.  We fit the fundamental plane by minimizing $\chi^2$ in, 
\begin{equation}
\chi^2 = \log R_0 - a \log \sigma - b \log I_0 - c
\end{equation}
where $R_0$ is the effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.  The resulting best-fit parameters are  a =1.376 , b = -0.661, c = -9.938.  We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply galaxies with similar magnitudes, colors, and redshifts to our GLSBs.   See \citet{Saulder13} for a more rigorous analysis of the Fundamental Plane in SDSS.

%Note that we are not correcting for Malmquist bias or biases in the SDSS spectroscopic selection criteria.  Our selection is simply for galaxies of a similar magnitude and redshift.

\subsection{GLSB Disks}
The diameters of these disks are very large.  Stellar disks are typically embedded in much larger \HI\ disks.  The size of the GLSB stellar disks is similar to the largest \HI\ disks observed in nearby galaxies, in support of the \citet{Mapelli08} model where the GLSB disks are the faded remnants of a normal \HI\ disk that has experienced a merger induced star-burst.

For comparison:  \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.  Maybe also look at THINGS data for comparisons on how large galaxy disks get.

Papers that have large \HI\ rotation curves that I might compare to:
\citet{DeBlok2008,Swaters09,Verheijen01}

In Figure~\ref{disk_comp}, we compare the sizes of the stellar disks of the GLSB galaxies with other observations.  For this plot, we take the maximum detected radius from the literature for the galaxies.  It is possible that deeper observations could increase the values of $R_{max}$.  While UGC 6614 close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.  This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems without some additional source of angular momentum.

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection.  It is interesing to note that the stellar disks of GLSB galaxies are often larger than the \HI\ disks of nearby systems.  \label{disk_comp}}
\end{figure}

\section{Kinematics}

%It would be nice to be able to use just the OII doublet to measure gas velocities from some of the galaxies.  Paper that discusses the range of OII ratio values in \citet{Wang04}.  Looks like it's usually around 0.5, but in low density regions it goes to 1.4.  Fuck.

It might be nice to spin this as a chance to measure the DM halo of ellipticals to very large radii.  Some relevant papers for comparison:
\citet{Weij09} use SAURON to get way out.  \citet{Proctor09} use Keck.  \citet{Murphy2011} use VP.

%$R_e = 7.3$\arcsec for UGC06614\\
%$R_e = 7.17$\arcsec for Malin2

The kinematics of the extended GLSB disks represents a unique probe for measuring the extended dark matter halo of elliptical galaxies.

We use the kinemetry package presented in \citet{Krajn06} to fit a tilted-ring model to the stellar kinematics.  For these fits, we hold the position angle and inclination fixed to values found from fitting the fiber-photometry.  Figures~\ref{malin_kinem} and~\ref{ugc_kinem} show the kinemetry fits and extracted rotation curves.  We iterate the fit, clipping residuals which deviate from the model my more than 250 \kms.

While we are making rather sweeping assumptions about the nature of the GLSB disks by fitting a simple disk with fixed position angle and inclination, the fits are quite good.  We also note that by observing disks, we do not have to worry about the velocity anisotropy parameter that traditionally makes dynamical modeling of ellipticals difficult.

Notes on individual rotation curves:
The Malin 2 rotation curve is rather complicated, having several abrupt rises.  This is especially strange given the very smooth photometric profile.  UGC 6614, on the other hand, has a relatively normal spiral galaxy-like rotation curve that rises linearly out to 10 kpc and then flattens.

The lack of rotation in the central regions of the galaxies is not particularly surprising, as this is the region that is flux-dominated by the central elliptical galaxy.  XXX-that hopefully we have data that shows they are not rotating or rotating in a different orientation.

The extracted rotation curves imply large dark matter halos.  For Malin 2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).  For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of$0.46\times 10^{11} \msun$ ).

%using /astro/store/shared-scratch1/yoachim/Research/GLSB/Analysis/mass_estm.pro
If we use the circular speed of the \HI\ data, we end up with masses of $25\times 10^{11} \msun$ for Malin 2 and $6.5\times 10^{11} \msun$ for UGC 6614.  So that's dynamical to stellar mass ratios of 18 and 14 respectively.  Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.

Thus, for Malin~2, we reach a radius of $\sim 6.2 R_e$, and find a dark matter fraction of 81\%.  For UGC 6614, we reach a radius of  $\sim 5.2 R_e$ and find a dark matter fraction of 71\%.

\citet{Murphy2011} reach $\sim2 R_e$ using just stellar data, and then rely on globular cluster kinematics to extended out to $5 R_e$.

XXX-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.  UGC 6614 is mostly emission from the center.

%print, rcmass(42.,280.)
%print, rcmass(17.,200.)

%scales=[0.940, 0.444] ;kpc/arcsec.  CMB frame from NED
%re = [7.17, 7.3] ;effective radii in arcsec

XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.

\section{Star Formation Histories}
Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.  We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.  This gives us 361 unique non-zero model spectra.

Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin 2 and UGC 06614.  Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.

The best fitting star formation histories are shown in Figures~\ref{sfh_malin2} and~\ref{sfh_ugc}, while the best fitting stellar metallicities are shown in Figures~\ref{metal_malin2} and~\ref{metal_ugc}.  We find that {\emph{both galaxies have stellar populations dominated by old stars at all radii}}.  While the outer disks have emission lines and have spectra that are best fit with some current star formation, the total stellar mass is still overwhelmingly dominated by old stars.  Both galaxies also show very steep metallicity gradients, with centers that are super-solar metallicity (at the limit of our models), while the outer disks are both best fit by [Z/H]=-0.7.

A problem with fitting observed galaxy spetra with templates is that residuals between the model and data are dominated by non-Gaussian systematic effects such as template mis-match and improper parameterization of the SFH.  Since the residuals are non-Guassian, there is no statistical formalism for generating uncertanties in the fit.  To generate our error bars, we look at the range of fits which have $\chi^2$ values within 100 of the minimum.  In many cases, this eliminates nearly all fits except for the minimum.  In these cases, we use the 4 best-fitting models to estimate the range of possible fits.

The dominance of an old stellar population at large radii seems to contradict the star-burst formation mechanism of \citet{Mapelli08}, and favor an accretion model where a galaxy already containing old stars is disrupted by a massive elliptical galaxy.

These are incredibly steep metallicity gradients.  The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin 2 and $\sim -0.68$ for UGC 6614.  These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12}.  Other cites for elliptical gradients \citep{Kuntschner10}

\section{Disk Progenitors}

It should be relatively easy to speculate about the galaxies that merged to form the disk. I can pull \HI\ masses, and then calc some stellar masses given the SDSS photometry and my own stellar M/L ratios.  Then given a baryonic mass and a typical stellar metallicity, it should be easy match that up to something.  Using baryonic TF relation, I'm getting pretty large $V_c$ values for what the accreted galaxy would have been.  I guess we could even speculate that this was a 3+ body encounter, so multiple gas rich systems that settle in.  That would help explain the low metallicities.

Figure~\ref{thingsMHI} shows the total \HI\ mass for galaxies observed in the THINGS survey \citep{Walter2008}, along with the \HI\ masses for GLSB galaxies \citep{Pickering97}.

We can't really use the stellar luminosity of the disk to constrian the projenitor since there are signs of current {\emph in situ} star formation in the disks.  However, the very low stellar metalicities point to low-mass projenitors.

Hard to estimate what the progenitor system of the disks were.  Is there a good plot of disk \HI\ mass and metallicity out there?  Might even need to measure Lick indices to try and get everything on the same metallicity system.

These systems are rare enough, that one might imagine rather complicated scenarios for creating them.  For example, a three-body enocounter could eject one galaxy while leaving a second in a nearly circular orbit.  Back of the envelope, a galaxy ejected at 5000 \kms would go 1.5 degrees per gigayear.  Even if the ejection was partly along the line of sight, it would be hard to find several gigayears later.  Unlike the collisional ring scenario where one would expect the galaxy that stimulated the ring formation to still be nearby.

The basic observational properties of GLSBs that need to be explained:
\begin{enumerate}
\item{These galaxies have \HI\ disks that extend much farther than typical spiral galaxies (Figure~\ref{disk_comp}). }
\item{While GLSBs have large disks, the total \HI\ mass in these disks is lower than expected given their rotational velocities (Figure~\ref{thingsMHI})}
\item{The central bulges are similar to elliptical galaxies in SDSS (Figure~\ref{elliptical_relations}).}
\item{The stellar populations in the centers of GLSBs are old and very metal rich.}
\item{The stellar populations in the extended disks shows some signs of ongoing star formation, but is consistent with being dominated by an old metal poor population.}
\end{enumerate}

%/astro/store/scratch/tmp/yoachim/Research/GLSB/THINGS/guess_projen.py
\begin{figure}
\epsscale{0.5}
\plotone{Plots/things_projenguess.eps}
\epsscale{1}
\caption{Comparison of GLSB \HI\ masses with \HI\ masses measured in the THINGS survey \citep{Walter2008}.  While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a $\sim$110 km/s galaxy, assuming the merger did not trigger large amounts of star formation and feedback. \label{thingsMHI}}
\end{figure}

\section{Discussion}

We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.

An accretion formation scenario does the best job explaining all the observations.  While a collisional ring could fade to a GLSB, the stellar population should be relatively young, and one might not expect a steep metallicity gradient.  Also, there are no obvious galaxies near GLSBs to act as progenitor colliders.

It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.  It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.

Accretion can also form GLSB systems around any type of host galaxy, explaining how \citet{Barth07} can find that Malin~1 is an SB0 galaxy, while our two systems are normal ellipticals.

Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.  We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.

If these systems do prove to be ellipticals with accreted high angular momentum disks, they represent an amazing opportunity to probe the dark matter halo properties of elliptical systems to very large radii.

Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.  Also see \citet{Capp11} that says slow rotators are very rare in the field.  So it might be strange if Malin 2 and UGC 6614 are slow rotators...

\section{Conclusions}

We have observed two giant low surface brightness galaxies with the VIRUS-P IFU.  We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a lareg disk.  The stellar stars have a disk-like velocity field, and are dominated by old stars, but do show signs of ongoing star formation.

In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit specta from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.  This data will also help up build dynamicall models for the systems.

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs.  Thanks to the observing specialists at Apache Point for their help executing our remote observations.

This paper includes data taken at The McDonald Observatory of The University of Texas at Austin.

Based on observations obtained with the Apache Point Observatory
3.5-meter telescope, which is owned and operated by the Astrophysical
Research Consortium.

This research made use of the ``K-corrections calculator'' service available at http://kcor.sai.msu.ru/

GANDALF was developed by the SAURON team and is available from the SAURON website (www.strw.leidenuniv.nl/sauron). See also Sarzi et al. (2006, MNRAS, 366, 1151) for details.

Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, and the U.S. Department of Energy Office of Science. The SDSS-III web site is http://www.sdss3.org/.

SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven National Laboratory, University of Cambridge, Carnegie Mellon University, University of Florida, the French Participation Group, the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New York University, Ohio State University, Pennsylvania State University, University of Portsmouth, Princeton University, the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, University of Washington, and Yale University.

%\bibliography{/astro/users/yoachim/Dropbox/Papers/Bib_files/big_jabref}
\bibliography{/Users/yoachim/Dropbox/Papers/Bib_files/big_jabref.bib}

\begin{figure}
\plottwo{Plots/sdssbinned_Malin2.eps}{Plots/Malin2mu.eps}
\epsscale{.5}
\plotone{Plots/Malin2profile_fit.eps}
\epsscale{1}
\caption{Upper Left:  SDSS image of Malin 2.  Upper Right:  Image made with the VIRUS-P datacube.  Lower:  An exponential fit to the fiber magnitudes.  Red points show fibers that were clipped while the solid line shows the best-fit.  }
\end{figure}

%\begin{figure}
%%\plottwo{Plots/Malin2stellarv.eps}{Plots/Malin2disp.eps}\\
%%\epsscale{0.5}
%\plottwo{Plots/Malin2stellarv.eps}{Plots/binned_Malin2svmap.eps}
%%\epsscale{1}
%\caption{Stellar kinematics.}
%\end{figure}

%\begin{figure}
%\plottwo{Plots/sellarv_trimmed_malin2.eps}{Plots/rc_malin2.eps} \\
%\plottwo{Plots/binned_stelv_trimmed_malin2.eps}{Plots/binned_rc_trimmed_malin2.eps}
%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
%\end{figure}
%XXX-do an actual tilted ring fit to this shit.

\begin{figure}
\epsscale{0.25}
\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps}
\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
\caption{Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.  The dashed curve shows the expected stellar mass contribution to the rotation curve.  Vertical lines mark $R_e$ and $5R_e$.  \HI\ data from \citet{Pickering97}.  \label{malin_kinem}}
\end{figure}

%\begin{figure}
%\epsscale{0.25}
%\plotone{Plots/oii_fluxMalin2.eps}\plotone{Plots/oiii_fluxMalin2.eps}\plotone{Plots/hbfluxMalin2.eps}
%\plotone{Plots/oii_fluxbinned_Malin2.eps}\plotone{Plots/oiii_fluxbinned_Malin2.eps}\plotone{Plots/hbfluxbinned_Malin2.eps}
%\epsscale{1}
%\caption{Emission line maps.}
%\end{figure}

\begin{figure}
\plottwo{Plots/Malin2bin_map.eps}{Plots/Malin2binned_spec.eps}
\caption{Left:  Map of which fibers were binned together.  Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked. \label{malin2_binmap}}
\end{figure}

%\begin{figure}
%\plottwo{Plots/rsfr_ebMalin2.eps}{Plots/rel_ebMalin2.eps}
%\caption{The best fitting star formation histories and resulting total stellar masses.  \label{sfh_malin2}}
%\end{figure}

%\begin{figure}
%\epsscale{.5}
%\plotone{Plots/Malin2zgrad.eps}
%\epsscale{1}
%\caption{Stellar metallicity gradient. \label{metal_malin2}}
%\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Plots/Malin2_chibar_sfr.eps}
\epsscale{1}
\caption{ Best fitting star formation histories.  For each bin, the SFH is normalized by the peak at each radius.  Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.  \label{sfh_malin2} }
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Plots/Malin2_chibar_z.eps}
\epsscale{1}
\caption{Best fitting stellar metallicities.   Dashed line shows the maximum model metallicity used in the models (minimum is below the y range).  Error bars are as in Figure~\ref{sfh_malin2}. \label{metal_malin2}}
\end{figure}

\begin{figure}
\plottwo{Plots/sdssbinned_UGC06614.eps}{Plots/UGC06614mu.eps}
\epsscale{0.5}
\plotone{Plots/UGC06614profile_fit.eps}
\epsscale{1}
\caption{Upper Left:  SDSS image of UGC 06614.  Upper Right:  Image made with the VIRUS-P datacube.  Lower:  An exponential fit to the fiber magnitudes.  Red points show fibers that were clipped while the solid line shows the best-fit.  We only included fibers beyond the outer ring structure.  }
\end{figure}

%\begin{figure}
%%\plottwo{Plots/UGC06614stellarv.eps}{Plots/UGC06614disp.eps}\\
%%\epsscale{0.5}
%\plottwo{Plots/UGC06614svmap.eps}{Plots/binned_UGC06614svmap.eps}
%%\epsscale{1}
%\caption{Stellar kinematics.}
%\end{figure}

%\begin{figure}
%\plottwo{Plots/sellarv_trimmed_UGC06614.eps}{Plots/rc_UGC06614.eps}
%\plottwo{Plots/binned_stelv_trimmed_binned_UGC06614.eps}{Plots/binned_rc_trimmed_binned_UGC06614.eps} \\
%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
%\end{figure}

\begin{figure}
\plottwo{Plots/UGC06614bin_map.eps}{Plots/UGC06614binned_spec.eps}
\caption{Left:  Map showing which fibers were binned for UGC 6614.  Right:  The binned spectra, color-coded to match the map on the left. \label{ugc_binmap}}
\end{figure}

%\begin{figure}
%\plottwo{Plots/rsfr_ebUGC06614.eps}{Plots/rel_ebUGC06614.eps}
%\caption{The best fitting star formation histories and resulting total stellar mass fractions.   For all radial bins, the stellar mass is dominated by stars older than 2 Gyr.  Error bars represent the best XXX fitting models.  \label{sfh_ugc} }
%\end{figure}

%\begin{figure}
%\epsscale{.5}
%\plotone{Plots/UGC06614zgrad.eps}
%\epsscale{1}
%\caption{Stellar metallicity gradient.  \label{metal_ugc}}
%\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Plots/UGC06614_chibar_sfr.eps}
\caption{ Best fitting star formation histories.  For each bin, the SFH is normalized by the peak bin.  Error bars are based on $\Delta\chi^2=100$ or the 4 best fitting models, whichever provides more points.  \label{sfh_ugc} }
\epsscale{1}
\end{figure}

\begin{figure}
\epsscale{.5}
\plotone{Plots/UGC06614_chibar_z.eps}
\epsscale{1}
\caption{Best fitting stellar metallicities.   \label{metal_ugc}}
\end{figure}

\begin{figure}
\epsscale{0.25}
\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps}
\plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
\caption{Fitting the velocity maps with kinemetry package. Vertical lines mark $R_e$ and $5R_e$.  The dashed lines shows a rotation curve based in the enclosed flux, normalized so that all the SDSS stellar mass is contained within $3R_e$.  \HI\ data from \citet{Pickering97}.\label{ugc_kinem}}
\end{figure}

%\begin{figure}
%\epsscale{0.25}
%\plotone{Plots/oii_fluxUGC06614.eps}\plotone{Plots/oiii_fluxUGC06614.eps}\plotone{Plots/hbfluxUGC06614.eps}
%\plotone{Plots/oii_fluxbinned_UGC06614.eps}\plotone{Plots/oiii_fluxbinned_UGC06614.eps}\plotone{Plots/hbfluxbinned_UGC06614.eps}
%\epsscale{1}
%\caption{Emission line maps.}
%\end{figure}

%\begin{figure}
%\epsscale{.5}
%\caption{ \emph{continued}.}
%\end{figure}

\clearpage

\appendix
\section{SDSS SQL quarries} \label{SQL}
To build our sample of comparison galaxies from SDSS, we used the CasJobs interface to query the SDSS DR10 database.

the galaxy CMD contours in Figure~\ref{elliptical_relations} were obtained via:
%gal_cmd_2
\begin{verbatim}
select 
objid,ra,dec,
dered_u,dered_g,dered_r,dered_i,dered_z,
z,4.27E+3*z as d_hubble_mpc,
dered_u-dered_r as u_minus_r,
dered_r-5*log10(4.27E+8*z) as abs_mag_r

from specphotoall
where
class='GALAXY'
AND dered_r between 13.5 and 17.7
AND ((flags & 0x10000000) != 0)
AND ((flags & 0x8100000c00a0) = 0)
AND (((flags & 0x400000000000) = 0) or (psfmagerr_g <= 0.2))
AND (((flags & 0x100000000000) = 0) or (flags & 0x1000) = 0)
AND zerr < 0.05
AND z BETWEEN 0.01 and 0.085
AND dered_r - 5*log10(4.27E+08*z) BETWEEN -23.5 and -15.5
\end{verbatim}

The Fundamental Plane contours in Figure~\ref{elliptical_relations} was computed from:
%fund_2
\begin{verbatim}
select
ph.objid, sp.z, sp.velDisp, sp.velDisperr, deVMag_g,deVMag_r, ph.deVRad_r, 
ph.r,ph.dered_r, ph.extinction_r, ph.extinction_g, ph.deVAB_r,  gs.best_model_z, 
gse.oh_p50, gse.lgm_tot_p50, gs.model_chisq_040, gs.model_chisq_080, 
gs.model_chisq_170, gs.model_chisq_400, zoo.spiral, zoo.elliptical, 
zoo.uncertain, zoo.p_el, zoo.p_cw,zoo.p_acw

from specobj as sp, photoobj as ph, galSpecIndx as gs, 
galSpecExtra as gse, zoospec as zoo

where
sp.bestObjID = ph.objID and gs.specObjID = sp.specObjID 
and gse.specObjID = sp.specObjID 
and zoo.objid =  ph.objID

AND sp.class='GALAXY'
AND sp.velDisp != 0
AND sp.z BETWEEN 0.01 and 0.085
AND sp.zerr < 0.05
AND ph.dered_r between 13.5 and 17.7
AND ph.dered_u-ph.dered_r > 2.1
AND ph.lnLDeV_r-ph.lnLExp_r > 0.29559
AND ph.petroR90_i/ph.petroR50_i > 2.5
AND ((ph.flags & 0x10000000) != 0)
AND ((ph.flags & 0x8100000c00a0) = 0)
AND (((ph.flags & 0x400000000000) = 0) or (ph.psfmagerr_g <= 0.2))
AND (((ph.flags & 0x100000000000) = 0) or (ph.flags & 0x1000) = 0)
\end{verbatim}

Finally, the mass-metallicity relation in Figure~\ref{elliptical_relations} was obtained via:
%lick_combo_v4
\begin{verbatim}
select 
ph.objid,sp.velDisp, gse.lgm_tot_p50, gs.lick_hd_a_sub, gs.lick_hd_f_sub, 
gs.lick_cn1_sub, gs.lick_cn2_sub, gs.lick_Ca4227_sub, gs.lick_G4300_sub, 
gs.lick_hg_a_sub, gs.lick_hg_f_sub, gs.lick_fe4383_sub, gs.lick_ca4455_sub, 
gs.lick_fe4531_sub, gs.lick_c4668_sub, gs.lick_hb_sub, gs.lick_fe5015_sub, 
gs.lick_mg1_sub, gs.lick_mg2_sub, gs.lick_mgb_sub, gs.lick_Fe5270_sub, 
gs.lick_Fe5335_sub, gs.lick_Fe5406_sub, gs.lick_Fe5709_sub, gs.lick_Fe5782_sub, 
gs.lick_NaD_sub, gs.lick_TiO1_sub, gs.lick_TiO2_sub

from specobj as sp, photoobj as ph, galSpecIndx as gs, galSpecExtra as gse

where
sp.bestObjID = ph.objID and gs.specObjID = sp.specObjID 
and gse.specObjID = sp.specObjID
AND sp.class='GALAXY'
AND sp.velDisp != 0
AND sp.z BETWEEN 0.01 and 0.085
AND sp.zerr < 0.05
AND ph.dered_r between 13.5 and 17.7
AND ph.dered_u-ph.dered_r > 2.1
AND ph.lnLDeV_r-ph.lnLExp_r > 0.29559
AND ph.petroR90_i/ph.petroR50_i > 2.5
AND ((ph.flags & 0x10000000) != 0)
AND ((ph.flags & 0x8100000c00a0) = 0)
AND (((ph.flags & 0x400000000000) = 0) or (ph.psfmagerr_g <= 0.2))
AND (((ph.flags & 0x100000000000) = 0) or (ph.flags & 0x1000) = 0)
\end{verbatim}

\end{document}

% LocalWords:  Debattista Horrocks Lancashire RCUK Malin Stanonik Spavone Lelli
% LocalWords:  Bothun GLSB Das Mapelli Weij Shmitz Loebman SungWon Kwak Scd Sd
% LocalWords:  Schiminovich Iodice Belokurov Fairchild RMS pPXF Cappellari th
% LocalWords:  GANDALF Sarzi CosmoloPy Bernardi GLSBs DeBlok Verheijen Yoachim
% LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA PR1 DM
% LocalWords:  2HE IFU UGC HSB S0 SAURON ellipticals SB0 M31 Malin2 Spitzer IC
% LocalWords:  kpc HIPASS CCD metallicity MANGA 0pt SDSS arcsec lensing 7m IRAF
% LocalWords:  Spectrograph spectrograph IDL longslit photometric FWHM SSP mis
% LocalWords:  dispersions Balmer decrement DR10 fiducial WMAP7 BAO H0 redshift
% LocalWords:  Faber Mg2 redshifts NGC kinemetry photometry anisotropy Gyr SFH
% LocalWords:  metallicities colliders rotators et al MNRAS de datacube Ppxf
% LocalWords:  dashed

### 2015-04-12 Plots/pull_plots.sh

@@ -1,0 +1,10 @@
+rsync -ar ~/Research/GLSB/Analysis/Plots/* /astro/users/yoachim/Dropbox/Writing/GLSB/Plots/
+
+rsync -ar ~/Research/GLSB/THINGS/*.eps /astro/users/yoachim/Dropbox/Writing/GLSB/Plots/
+
+rsync -ar ~/Research/GLSB/SDSS/dr10/*.eps /astro/users/yoachim/Dropbox/Writing/GLSB/Plots/
+
+#rsync -ar ~/Research/GLSB/SDSS/Color_Magnitu_Diagram.eps /astro/users/yoachim/Dropbox/Writing/GLSB/Plots/
+
+#rsync -ar ~/Research/GLSB/SDSS/mg_sigma.eps /astro/users/yoachim/Dropbox/Writing/GLSB/Plots/
+

### 2015-04-13 glsb.tex
edits

@@
 
-Both our objects have been observed with SDSS, making it possible to compare them to a large number of systems.
+Both of our objects have been observed with SDSS, making it possible to compare them to a large number of systems.
 The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.
@@
 Throughout, we use the CosmoloPy\footnote{\url{http://roban.github.com/CosmoloPy/}} fiducial cosmology ($h=0.704$, $\Omega_{m_0}=0.2726$, $\Omega_{\lambda_0}=0.7274$).
+Note that we are not correcting for Malmquist bias or biases in the SDSS spectroscopic selection criteria.
+Our selection is simply for galaxies of a similar magnitude and redshift.
 
@@
 We use extinction corrected magnitudes and $k$-corrected colors\citep{Chilingarian10}.
-Both of our GLSBs lie on the red-sequence in a color-magnitude diagram.
+Both of our GLSBs lie on the red-sequence in the color-magnitude diagram.
 
-The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the GLSBs are on the bright end of the red-sequence.
+The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.
 
@@
 See \citet{Saulder13} for a more rigorous analysis of the Fundamental Plane in SDSS.
-
-%Note that we are not correcting for Malmquist bias or biases in the SDSS spectroscopic selection criteria.  Our selection is simply for galaxies of a similar magnitude and redshift.
 
@@
 
-XXX-crap, whatever happened to the gas kinematics?
+%XXX-crap, whatever happened to the gas kinematics?
 There are emission lines out there--are they bright enough to get in single fibers of not?
@@
 XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
+
+XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confim they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
 

### 2015-04-13 glsb.tex
a

@@
 
-\title{Giant Low Surface Brightness Galaxies as Merger Remnants}
+\title{Giant Low Surface Brightness Galaxies As Merger Remnants}
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Shmitz\altaffilmark{1}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
+\author{Peter Yoachim\altaffilmark{1}, Denise Shmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
   }
@@
 \altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}
+\altaffiltext{4}{XXX-cal tech}
 
@@
 We use the b-spline procedure described in \citet{Kelson03} to generate background frames.
-The corners of each frame contain enough empty fibers to measure the sky background in each exposure.
+The corners contain enough empty fibers to measure the sky background in each exposure.
 Because we bin fibers together, imperfect sky-subtraction represents a serious source of potential systematic errors.
@@
 
-In addition to individual fibers, we have binned neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers.
+In addition to individual fibers, we have binned sets of three neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers.
+The fiber surface brightnesses are plotted in Figures~\ref{Malin2_fibers} and~\ref{ugc_fibers}, and the pPXF stellar velocity maps are shown in Figures~\ref{malin_kinem} and~\ref{ugc_kinem}.
 
@@
 Figure~\ref{elliptical_relations} shows where the GLSBs fall on the major galaxy relations.
-We use extinction corrected magnitudes and $k$-corrected colors\citep{Chilingarian10}.
+We use extinction corrected magnitudes and $k$-corrected colors \citep{Chilingarian10}.
 Both of our GLSBs lie on the red-sequence in the color-magnitude diagram.
@@
 \subsection{GLSB Disks}
-The diameters of these disks are very large.
+
+The diameters of GLSB disks are very large, with Malin~1's stellar dist detected out to a radius of 115 kpc \citep{Moore06}.
 Stellar disks are typically embedded in much larger \HI\ disks.
@@
 
-For comparison:  \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.  Maybe also look at THINGS data for comparisons on how large galaxy disks get.
+For comparison:  \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.
 
@@
 It is possible that deeper observations could increase the values of $R_{max}$.
-While UGC 6614 close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.
+While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.
 This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems without some additional source of angular momentum.
@@
 THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum redius with a stellar flux detection for the GLSB galaxies.
 It is interesing to note that the stellar disks of GLSB galaxies are often larger than the \HI\ disks of nearby systems.
@@
 \epsscale{1}
-\caption{Comparison of GLSB \HI\ masses with \HI\ masses measured in the THINGS survey \citep{Walter2008}.
+\caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.
 While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a $\sim$110 km/s galaxy, assuming the merger did not trigger large amounts of star formation and feedback.
@@
 Red points show fibers that were clipped while the solid line shows the best-fit.
-}
+\label{Malin2_fibers} }
 \end{figure}
@@
 We only included fibers beyond the outer ring structure.
-}
+\label{ugc_fibers} }
 \end{figure}

### 2015-04-14 glsb.tex
fixed spelling

@@
 
-GLSBs are typically classified as spriral galaxies \citep{Das13}, however, high resolution imaging of Malin~1 has shown that the central region appears to be a normal
+GLSBs are typically classified as spiral galaxies \citep{Das13}, however, high resolution imaging of Malin~1 has shown that the central region appears to be a normal
 
@@
 \citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.
-They think the gas and star formation is comming from minor mergers or accretion.
+They think the gas and star formation is coming from minor mergers or accretion.
 
@@
 
-To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddned $r$ magnitude between 13.5 and 17.7.
+To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddened $r$ magnitude between 13.5 and 17.7.
 When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology selectors).
 These are simply galaxies for comparison, not a rigorously defined volume-complete sample.
-Our full SQL querries are shown in \S\ref{SQL}.
+Our full SQL queries are shown in \S\ref{SQL}.
 This gives us a sample of 141,001 objects, 45,703 of which have red colors.
@@
 THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum redius with a stellar flux detection for the GLSB galaxies.
-It is interesing to note that the stellar disks of GLSB galaxies are often larger than the \HI\ disks of nearby systems.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum radius with a stellar flux detection for the GLSB galaxies.
+It is interesting to note that the stellar disks of GLSB galaxies are often larger than the \HI\ disks of nearby systems.
 \label{disk_comp}}
@@
 
-XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confim they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
+XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
 
@@
 
-A problem with fitting observed galaxy spetra with templates is that residuals between the model and data are dominated by non-Gaussian systematic effects such as template mis-match and improper parameterization of the SFH.
-Since the residuals are non-Guassian, there is no statistical formalism for generating uncertanties in the fit.
+A problem with fitting observed galaxy spectra with templates is that residuals between the model and data are dominated by non-Gaussian systematic effects such as template mis-match and improper parameterization of the SFH.
+Since the residuals are non-Gaussian, there is no statistical formalism for generating uncertainties in the fit.
 To generate our error bars, we look at the range of fits which have $\chi^2$ values within 100 of the minimum.
@@
 
-We can't really use the stellar luminosity of the disk to constrian the projenitor since there are signs of current {\emph in situ} star formation in the disks.
-However, the very low stellar metalicities point to low-mass projenitors.
+We can't really use the stellar luminosity of the disk to constrain the progenitor since there are signs of current {\emph in situ} star formation in the disks.
+However, the very low stellar metallicities point to low-mass progenitors.
 
@@
 These systems are rare enough, that one might imagine rather complicated scenarios for creating them.
-For example, a three-body enocounter could eject one galaxy while leaving a second in a nearly circular orbit.
+For example, a three-body encounter could eject one galaxy while leaving a second in a nearly circular orbit.
 Back of the envelope, a galaxy ejected at 5000 \kms would go 1.5 degrees per gigayear.
@@
 We have observed two giant low surface brightness galaxies with the VIRUS-P IFU.
-We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a lareg disk.
+We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a large disk.
 The stellar stars have a disk-like velocity field, and are dominated by old stars, but do show signs of ongoing star formation.
 
-In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit specta from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.
-This data will also help up build dynamicall models for the systems.
+In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit spectra from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.
+This data will also help up build dynamical models for the systems.
 
@@
 % LocalWords:  metallicities colliders rotators et al MNRAS de datacube Ppxf
-% LocalWords:  dashed
+% LocalWords:  dashed CDM Kasparova LSB Dutton Raskutti Sa Morganti
+%%  LocalWords:  Emonts Weijmans Ibata McConnachie Schweizer Magain
+%%  LocalWords:  Oosterloo baryonic Buote GALEX Salim Kelson outlier
+%%  LocalWords:  Bruzual Ahn Willett SQL Chilingarian Saulder Swaters
+%%  LocalWords:  Krajn GN Kuntschner situ indices Emsell Capp CasJobs

### 2015-04-14 glsb.tex
ack

@@
 \caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.
-While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a $\sim$110 km/s galaxy, assuming the merger did not trigger large amounts of star formation and feedback.
+While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}$\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback.
 \label{thingsMHI}}
@@
 \acknowledgments
-Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs.  Thanks to the observing specialists at Apache Point for their help executing our remote observations.
+Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. 
+%Thanks to the observing specialists at Apache Point for their help executing our remote observations.
 
@@
 
-Based on observations obtained with the Apache Point Observatory
-3.5-meter telescope, which is owned and operated by the Astrophysical
-Research Consortium.
+%Based on observations obtained with the Apache Point Observatory
+%3.5-meter telescope, which is owned and operated by the Astrophysical
+%Research Consortium.
 

### 2015-04-16 glsb.tex
outline intro

@@
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Shmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
+\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
   }
@@
 Meanwhile, observers tend to classify GLSB systems as normal spirals.
-\citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.
+\citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.
 Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.
@@
 XXX-add discussion of possibility the centers of GLSBs are normal galaxies.
+
+Points to cover in intro
+\begin{itemize}
+\item{GLSB galaxies are really big spirals}
+\item{Typically classified as extreme spirals observaionally}
+\item{but HST observations of Malin~1 show it is a regular galaxy with a distinct extended disk \citet{Barth07}}
+\item{Models for GLSB formation}
+  \begin{itemize}
+  \item{regular growth (maybe like polar ring galaxies, or just the large end of spirals)}
+  \item{faded collisional ring. \citet{Mapelli08, Mapelli12} }
+  \item{high angular momentum accretion event. \citet{Pen06}}
+  \end{itemize}
+  \item{Discuss how, if GLSBs are merger remnents, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
+\end{itemize}
 
@@
 
-\citet{Ibata05} look at extended disk of M31.
+%\citet{Ibata05} look at extended disk of M31.
+%\citet{Ibata13} claim M31 satellites are co-planer.  
+%\citet{McConnachie09} M31 survey showing lots of merger structure.
 
-\citet{Ibata13} claim M31 satellites are co-planer.
+%Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html
+%another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm
 
-\citet{McConnachie09} M31 survey showing lots of merger structure.
-
-Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html
-
-another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm
-
-From \citet{Matthews01b}, \HI\ measurements on the gals:
+%From \citet{Matthews01b}, \HI\ measurements on the gals:
 %name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
@@
 %UGC 6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
-\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.
+%\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.
 I'll need to compare my stellar kinematics to the \HI\ kinematics.
@@
 
-\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.
-
-\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.
-
-\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.
+%\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.  
+%\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.  
+%\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.
 They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.
@@
 \caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.
-While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}$\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback.
+While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback.
 \label{thingsMHI}}

### 2015-04-16 glsb.tex
discussion outline

@@
 \citet{Buote12} review of dark matter in ellipticals from x-ray observations.
-
-XXX-clearly need to look up bulge-to-disk metallicity gradient.
-Lauren did it with colors in \citet{MacArthur04}.
-Nice look with metallicity gradients as a function of scale-length, and kpc, and vrot and galaxy type.
-Did spectra gradients in \citet{MacArthur09}.
-MANGA would make this easy to compare...Maybe there's a SAURON paper on metallicity gradients.
 
@@
 \section{Star Formation Histories}
+
 Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.
@@
 
+Outline for discussion section
+\begin{itemize}
+\item{We find the GLSB systems Malin~2 and UGC~6614 are observationally most consistent with being normal elliptical galaxies that have undergone a high angular momentum minor merger with a gas rich system.}
+\item{recap photometric evidence--the centers look just like SDSS ellipticals.}
+\item{recap star formation histories. Disk is dominated by old stars.}
+\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.}
+\item{extended comparison to \citet{Kasparova14}}
+  \begin{itemize}
+    \item{Mass model of Malin~2 requires a huge isothermal core radius.}
+    \item{They measure gas metallicities and find solar in the center and half-solar at 20-30 kpc.
+While it is a fool's errand to compare metallicities between stars and gas, it is interesting that the gas metallicity gradient is much smaller than in the stars.
+If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.
+Hmm, looking at DR12 stuff, the pipeline reducitons are fitting solar metallicity to the center, not sure I believe that.
+}
+      \item{They have a nice mass-model that becomes dark matter dominated at around r=20 kpc.  Could this be the normal shape of elliptical dark matter halos?}
+  \end{itemize}
+
+\item{This could be the strongest evidence for very massive elliptical dark matter halos. }
+  \item{plan on getting higher spatial resolution spectra of the centers to confirm they are typical elliptical galaxies.}
+\end{itemize}
+
 We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.
@@
 
-Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.
+%Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.
 We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.
@@
 Also see \citet{Capp11} that says slow rotators are very rare in the field.
-So it might be strange if Malin 2 and UGC 6614 are slow rotators...
+So it might be strange if Malin 2 and UGC 6614 are slow rotators.
+
+XXX-clearly need to look up bulge-to-disk metallicity gradient.
+Lauren did it with colors in \citet{MacArthur04}.
+Nice look with metallicity gradients as a function of scale-length, and kpc, and vrot and galaxy type.
+Did spectra gradients in \citet{MacArthur09}.
+MANGA would make this easy to compare...Maybe there's a SAURON paper on metallicity gradients.
 

### 2015-04-24 glsb.tex
blah
working on intro

@@
 \altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}
-\altaffiltext{4}{XXX-cal tech}
+\altaffiltext{4}{XXX-Cal Tech}
 
@@
 Low surface brightness (LSB) galaxies are typically defined as disks with central surface brightnesses fainter than 23 $B$ mag arcsec$^2$.
-These disks are incredibly large, with Malin~1 being detected to a radius of over 100 kpc \citep{Moore06}.
-It is difficult to imagine how a stellar disk could form within a merger-driven $\Lambda$CDM cosmology.
+While LSB galaxies span a wide range of sizes and masses, the few giant low surface brightness that have been discovered seem to be unrelated objects that are at least an order of magnitude larger in extent than typical LSB systems (XXX-cite).
 
-A wide variety of formation scenarios have been proposed for GLSB systems.  \citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies xxx-expand this a bit.
-
-Meanwhile, observers tend to classify GLSB systems as normal spirals.
+Observers tend to classify GLSB systems as normal spirals.
 \citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.
 Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.
+Even the Galaxy Zoo project classifies GLSB galaxies as spirals.
+
+The disks in GLSB systems are incredibly large, with Malin~1 being detected to a radius of over 100 kpc \citep{Moore06}.
+Disks of this size are a challenge for typicall $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.
+\citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies xxx-expand this a bit.
+In their model, a collision where a thingy hits thuswise, blah blah, sets off an expanding ring of star formation.
+As this the star formation subsides and the stetllar population ages, it fades to form a disk that resembles in size and exponential profile observed GLSBs.
+XXX--also tie in \citep{Mapelli12}.
 
@@
 I think I can show that no, they are really normal elliptical galaxies that happen to have accreted disks.
-
-Standard catalogs list these systems as Sd and Sa galaxies, so they are commonly thought of as spirals.
 
@@
 \item{recap star formation histories. Disk is dominated by old stars.}
-\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.}
+\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.
+      \citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
+Lots of good stuff on fast/slow rotators.
+Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.
+They don't see any sharp transition like I do, all very smooth age and metal curves.
+}
 \item{extended comparison to \citet{Kasparova14}}

### 2015-04-28 glsb.tex
add new greene paper
put in bib file
fixed spell checking

@@
 Even the Galaxy Zoo project classifies GLSB galaxies as spirals.
+While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.
 
 The disks in GLSB systems are incredibly large, with Malin~1 being detected to a radius of over 100 kpc \citep{Moore06}.
-Disks of this size are a challenge for typicall $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.
-\citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies xxx-expand this a bit.
-In their model, a collision where a thingy hits thuswise, blah blah, sets off an expanding ring of star formation.
-As this the star formation subsides and the stetllar population ages, it fades to form a disk that resembles in size and exponential profile observed GLSBs.
-XXX--also tie in \citep{Mapelli12}.
+Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.
+\citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies.
+In their model, a collision sets off an expanding ring of star formation.
+As this the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.
+XXX-one problem is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.
 
 XXX-add discussion of possibility the centers of GLSBs are normal galaxies.
+
+\citet{Barth07} analyze HST imaging of Malin 1 and find that the central object is well described as a normal SB0/a galaxy.
+Makes good point that lots of the other large disk observations look like they are extensions of the inner galaxy, while Malin 1's disk is probably a distinct component.
 
@@
 \item{GLSB galaxies are really big spirals}
-\item{Typically classified as extreme spirals observaionally}
+\item{Typically classified as extreme spirals obsessionally}
 \item{but HST observations of Malin~1 show it is a regular galaxy with a distinct extended disk \citet{Barth07}}
@@
   \end{itemize}
-  \item{Discuss how, if GLSBs are merger remnents, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
+  \item{Discuss how, if GLSBs are merger remnants, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
 \end{itemize}
@@
 \citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.
-
-\citet{Barth07} analyze HST imaging of Malin 1 and find that the central object is well described as a normal SB0/a galaxy.
-Makes good point that lots of the other large disk observations look like they are extensions of the inner galaxy, while Malin 1's disk is probably a distinct component.
 
@@
 The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin 2 and $\sim -0.68$ for UGC 6614.
-These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12}.
+These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
 Other cites for elliptical gradients \citep{Kuntschner10}
@@
 If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.
-Hmm, looking at DR12 stuff, the pipeline reducitons are fitting solar metallicity to the center, not sure I believe that.
+Hmm, looking at DR12 stuff, the pipeline reductions are fitting solar metallicity to the center, not sure I believe that.
 }
@@
 %\bibliography{/astro/users/yoachim/Dropbox/Papers/Bib_files/big_jabref}
-\bibliography{/Users/yoachim/Dropbox/Papers/Bib_files/big_jabref.bib}
+%\bibliography{/Users/yoachim/Dropbox/Papers/Bib_files/big_jabref.bib}
+\bibliography{big_jabref.bib}
 
@@
 % LocalWords:  Debattista Horrocks Lancashire RCUK Malin Stanonik Spavone Lelli
-% LocalWords:  Bothun GLSB Das Mapelli Weij Shmitz Loebman SungWon Kwak Scd Sd
+% LocalWords:  Bothun GLSB Das Mapelli Weij Loebman SungWon Kwak Scd Sd
 % LocalWords:  Schiminovich Iodice Belokurov Fairchild RMS pPXF Cappellari th
 % LocalWords:  GANDALF Sarzi CosmoloPy Bernardi GLSBs DeBlok Verheijen Yoachim
-% LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA PR1 DM
-% LocalWords:  2HE IFU UGC HSB S0 SAURON ellipticals SB0 M31 Malin2 Spitzer IC
-% LocalWords:  kpc HIPASS CCD metallicity MANGA 0pt SDSS arcsec lensing 7m IRAF
+% LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA DM
+% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC
+% LocalWords:  kpc HIPASS CCD metallicity MANGA SDSS arcsec lensing IRAF
 % LocalWords:  Spectrograph spectrograph IDL longslit photometric FWHM SSP mis
-% LocalWords:  dispersions Balmer decrement DR10 fiducial WMAP7 BAO H0 redshift
-% LocalWords:  Faber Mg2 redshifts NGC kinemetry photometry anisotropy Gyr SFH
+% LocalWords:  dispersions Balmer decrement fiducia redshift
+% LocalWords:  Faber redshifts NGC kinemetry photometry anisotropy Gyr SFH
 % LocalWords:  metallicities colliders rotators et al MNRAS de datacube Ppxf
@@
 %%  LocalWords:  Krajn GN Kuntschner situ indices Emsell Capp CasJobs
+%%  LocalWords:  Schmitz circ accrete jabref CMD

### 2015-05-05 glsb.tex
fill out intro

@@
 While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.
+(xxx-maybe make a plot of SDSS spiral scale lengths and plot the GLSB systems).
 
@@
 As this the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.
-XXX-one problem is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.
+One obvious problem with this scenario is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.
 
-XXX-add discussion of possibility the centers of GLSBs are normal galaxies.
+The final formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
+\citet{Pen06} find that extended disks can be formed via the disruption of dwarf galaxies.
+These simulated debrie disks have exponential profiles and extend out to 200 kpc from the central galaxy.
 
-\citet{Barth07} analyze HST imaging of Malin 1 and find that the central object is well described as a normal SB0/a galaxy.
-Makes good point that lots of the other large disk observations look like they are extensions of the inner galaxy, while Malin 1's disk is probably a distinct component.
+Observations of Malin~1 support the accretion model of GLSBs.
+\citet{Barth07} analyze HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging.
+\citet{Barth07} points out that exteded disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).
+
+If GLSB disks are indeed the remains of accreted dwarf galaxies, they represent a unique opportunity to observationally probe the outer regions of galaxy dark matter halos, especailly if they form around elliptical galaxies.
+The mass profiles of elliptical galaxies have been difficult to constrain since they lack the HI disks found around spirals.
 

### 2015-05-07 glsb.tex
blah

@@
 If GLSB disks are indeed the remains of accreted dwarf galaxies, they represent a unique opportunity to observationally probe the outer regions of galaxy dark matter halos, especailly if they form around elliptical galaxies.
-The mass profiles of elliptical galaxies have been difficult to constrain since they lack the HI disks found around spirals.
+The mass profiles of elliptical galaxies have been difficult to constrain since they lack the extended \HI\ disks found around spirals.
+As an example of how difficult it can be to measure the outer regions of ellipical galaxy kinematics, \citet{Murphy2011} model M87 out to $\sim$23 kpc with stellar kinematics and out to 51 kpc with globular clusters (or $R=4.8 R_e$, where $R_e$ is the effective radius of M87).
+\citet{Raskutti14} are also limited to measuring kinematics out to $\sim$2-5 $R_e$.
+
+In comparison, the stellar disk of Malin~2 extends beyond XXX (XXX $R_e$), and the HI disk reaches beyond 100 kpc (XXX $R_e$).
+These distances have occasionally been reached by x-ray observations \citep{Buote12}.
 
@@
 
-In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.
+%In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.
 
-The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.
+%The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.
 The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum.
@@
 
-GLSBs are typically classified as spiral galaxies \citep{Das13}, however, high resolution imaging of Malin~1 has shown that the central region appears to be a normal
-
-\citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
+%\citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
 Lots of good stuff on fast/slow rotators.
@@
 
-\citet{Pickering97} has the \HI\ rotation curves of these guys.
+%\citet{Pickering97} has the \HI\ rotation curves of these guys.
 For UGC 6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.
@@
 
-Can we say that the stars formed in a higher density environment and then got dispersed.
+%Can we say that the stars formed in a higher density environment and then got dispersed.
 
-\citet{Das13} look at the environments of GLSB systems.
+%\citet{Das13} look at the environments of GLSB systems.
 He says that GLSBs are an extreme form of late type spiral galaxies.
@@
 
-Nice paper on galaxies that live in voids and how one did manage to build a polar \HI\ disk with no stars: \citet{Stanonik09}
+%Nice paper on galaxies that live in voids and how one did manage to build a polar \HI\ disk with no stars: \citet{Stanonik09}
 
-Chemical abundances in a polar disk:  \citet{Spavone10}
+%Chemical abundances in a polar disk:  \citet{Spavone10}
 
-a near scoop by \citet{Lelli10}.
+%a near scoop by \citet{Lelli10}.
 They re-analyze \HI\ data on Malin 1 and one other.
@@
 
-\citet{Morganti97} look at an elliptical with an \HI\ disk.  Find a nice flat rotation curve.
-\citet{Emonts08}  Another massive \HI\ ring around an S0 galaxy.
-\citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.
-
-\citet{Pen06} look at forming extended disks by disrupting a dwarf galaxy.
+%\citet{Morganti97} look at an elliptical with an \HI\ disk.  Find a nice flat rotation curve.
+%\citet{Emonts08}  Another massive \HI\ ring around an S0 galaxy.
+%\citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.
 
@@
 
-\cite{Rahman2007} has Spitzer observations of a few GLSB galaxies.
+%\cite{Rahman2007} has Spitzer observations of a few GLSB galaxies.
 
-\citet{Das10} find CO in Malin 2.  Make some points about it being stable
+%\citet{Das10} find CO in Malin 2.  Make some points about it being stable
 
-\citet{Mapelli12} making ring galaxies from off center collisions.
-
-\citet{Mapelli08} look at if ring galaxies could evolve into GLSB systems.
+%\citet{Mapelli12} making ring galaxies from off center collisions.  
+%\citet{Mapelli08} look at if ring galaxies could evolve into GLSB systems.
 
@@
 
-\citet{Schweizer89} Do a similar study with IC 2006, where they observe an \HI\ ring around the elliptical galaxy to get the total mass at large radii.  Looks like they get out to about 12.5 kpc.
+%\citet{Schweizer89} Do a similar study with IC 2006, where they observe an \HI\ ring around the elliptical galaxy to get the total mass at large radii.  Looks like they get out to about 12.5 kpc.
 
-\citet{Oosterloo07} HIPASS detection of \HI\ gas around 30 early-type galaxies.
+%\citet{Oosterloo07} HIPASS detection of \HI\ gas around 30 early-type galaxies.
 Most have regular disk or ring kinematics.
@@
 
-\citet{Magain13} look at strong lenses around 25 ellipticals, and then claim they see no evidence for extended DM halos.
+%\citet{Magain13} look at strong lenses around 25 ellipticals, and then claim they see no evidence for extended DM halos.
 Confusing plot--Maybe they get out to 5 $R_{1/2}$?
@@
 
-\citet{Spray95} CCD imaging of 8 GLSB systems.
+%\citet{Spray95} CCD imaging of 8 GLSB systems.
 
-\citet{Morganti13} Do modeling of ellipticals with declining velocity dispersion profiles.  Good place to start looking for the best way to model the long-slit data.
+%\citet{Morganti13} Do modeling of ellipticals with declining velocity dispersion profiles.  Good place to start looking for the best way to model the long-slit data.
 
-\citet{Buote12} review of dark matter in ellipticals from x-ray observations.
+%\citet{Buote12} review of dark matter in ellipticals from x-ray observations.
 
-XXX-need to look up some Thilker papers on extended UV disks, since these objects could be similar.
+%XXX-need to look up some Thilker papers on extended UV disks, since these objects could be similar.
 From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).
@@
 
-\citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.
+%\citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.
 They think the gas and star formation is coming from minor mergers or accretion.
 
-\citet{Salim12} Finds 2 more GLSB type objects -- could be a sign that there are multiple routes to making GLSB systems.
+%\citet{Salim12} Finds 2 more GLSB type objects -- could be a sign that there are multiple routes to making GLSB systems.
 
@@
 
-The other way to measure the dark matter halo of an elliptical is to use gravitational lensing.  \citet{Belokurov07} find a large ring in SDSS.
+%The other way to measure the dark matter halo of an elliptical is to use gravitational lensing.  \citet{Belokurov07} find a large ring in SDSS.
 
@@
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
-Looking at the SDSS data, our GLSB galaxies appear as normal red elliptical galaxies.
+Looking at the SDSS data, our GLSB galaxies appear as realtively typical red elliptical galaxies.
 \label{elliptical_relations}}
@@
 THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum radius with a stellar flux detection for the GLSB galaxies.
-It is interesting to note that the stellar disks of GLSB galaxies are often larger than the \HI\ disks of nearby systems.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum radius with a stellar flux detection for Malin~1.
+It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.
 \label{disk_comp}}

### 2015-10-07 glsb.tex
minor updates

@@
 
-Points to cover in intro
-\begin{itemize}
-\item{GLSB galaxies are really big spirals}
-\item{Typically classified as extreme spirals obsessionally}
-\item{but HST observations of Malin~1 show it is a regular galaxy with a distinct extended disk \citet{Barth07}}
-\item{Models for GLSB formation}
-  \begin{itemize}
-  \item{regular growth (maybe like polar ring galaxies, or just the large end of spirals)}
-  \item{faded collisional ring. \citet{Mapelli08, Mapelli12} }
-  \item{high angular momentum accretion event. \citet{Pen06}}
-  \end{itemize}
-  \item{Discuss how, if GLSBs are merger remnants, they represent a unique possibility to trace the dark matter halo of elliptical galaxies.  }
-\end{itemize}
-
 %In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.
@@
 
-\citet{Kasparova14} has an amazing analysis of Malin 2.
+XXX-\citet{Kasparova14} has an amazing analysis of Malin 2.
 They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.
@@
 
-Both of our objects have been observed with SDSS, making it possible to compare them to a large number of systems.
+Both of our objects, as well as Malin 1, have been observed with SDSS, making it possible to compare them to a large number of systems.
 The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.
@@
 
-Papers that have large \HI\ rotation curves that I might compare to:
-\citet{DeBlok2008,Swaters09,Verheijen01}
+%Papers that have large \HI\ rotation curves that I might compare to:
+%\citet{DeBlok2008,Swaters09,Verheijen01}
 
@@
 THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies and the maximum radius with a stellar flux detection for Malin~1.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1.
 It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.
@@
 \appendix
-\section{SDSS SQL quarries} \label{SQL}
+\section{SDSS SQL Querries} \label{SQL}
 To build our sample of comparison galaxies from SDSS, we used the CasJobs interface to query the SDSS DR10 database.

### 2015-10-20 glsb.tex
update figure

@@
 We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.
-We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone a high angular momentum merger which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
+We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone a high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
 We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.
@@
 Low surface brightness (LSB) galaxies are typically defined as disks with central surface brightnesses fainter than 23 $B$ mag arcsec$^2$.
-While LSB galaxies span a wide range of sizes and masses, the few giant low surface brightness that have been discovered seem to be unrelated objects that are at least an order of magnitude larger in extent than typical LSB systems (XXX-cite).
+While LSB galaxies span a wide range of sizes and masses, the few giant low surface brightness that have been discovered seem to be unrelated objects that are at least an order of magnitude larger in extent than typical LSB systems.
 
@@
 While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.
-(xxx-maybe make a plot of SDSS spiral scale lengths and plot the GLSB systems).
 
-The disks in GLSB systems are incredibly large, with Malin~1 being detected to a radius of over 100 kpc \citep{Moore06}.
+The disks in GLSB systems are incredibly large, with Malin~1 being detected in $R$-band to a radius of over 100 kpc \citep{Moore06}.
 Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.
-\citet{Mapelli08} form GLSB-like galaxies via the fading of collisional ring galaxies.
+\citet{Mapelli08} form GLSB-like galaxies in simulations via the fading of collisional ring galaxies.
 In their model, a collision sets off an expanding ring of star formation.
@@
 
-The final formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
+The another formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
 \citet{Pen06} find that extended disks can be formed via the disruption of dwarf galaxies.
@@
 The mass profiles of elliptical galaxies have been difficult to constrain since they lack the extended \HI\ disks found around spirals.
-As an example of how difficult it can be to measure the outer regions of ellipical galaxy kinematics, \citet{Murphy2011} model M87 out to $\sim$23 kpc with stellar kinematics and out to 51 kpc with globular clusters (or $R=4.8 R_e$, where $R_e$ is the effective radius of M87).
+As an example of how difficult it can be to measure the outer regions of ellipical galaxy kinematics, \citet{Murphy2011} model M87 out to $\sim$23 kpc with stellar kinematics and out to 51 kpc with globular clusters (or $R=4.8 R_e$, where $R_e$ is the effective radius).
 \citet{Raskutti14} are also limited to measuring kinematics out to $\sim$2-5 $R_e$.
 
-In comparison, the stellar disk of Malin~2 extends beyond XXX (XXX $R_e$), and the HI disk reaches beyond 100 kpc (XXX $R_e$).
+In comparison, the stellar disk of Malin~2 extends beyond 40 kpc (5.9 $R_e$), and the HI disk reaches beyond 100 kpc (14.8 $R_e$).
 These distances have occasionally been reached by x-ray observations \citep{Buote12}.
@@
 \item{The central bulges are similar to elliptical galaxies in SDSS (Figure~\ref{elliptical_relations}).}
-\item{The stellar populations in the centers of GLSBs are old and very metal rich.}
-\item{The stellar populations in the extended disks shows some signs of ongoing star formation, but is consistent with being dominated by an old metal poor population.}
+\item{The stellar populations in the centers of GLSBs are old and very metal-rich.}
+\item{The stellar populations in the extended disks shows some signs of ongoing star formation, but is consistent with being dominated by an old metal-poor population.}
 \end{enumerate}
 
-%/astro/store/scratch/tmp/yoachim/Research/GLSB/THINGS/guess_projen.py
+%--now on new mac.  /Users/yoachim/Research/GLSB/THINGS/guess_projen.py
 \begin{figure}
@@
 We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a large disk.
-The stellar stars have a disk-like velocity field, and are dominated by old stars, but do show signs of ongoing star formation.
+We find the inner bulge is similar to elliptical galaxies found in SDSS.
+The stars have a disk-like velocity field, are dominated by old stars, but do show signs of ongoing star formation.
+The stars also show a sharp metalicity transition, consistent with the disk forming independently of the bulge.
+The \HI content of the disk is also consistent with coming from a low-mass accreted galaxy.
 
 In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit spectra from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.
-This data will also help up build dynamical models for the systems.
 

### 2015-12-05 glsb.tex
fund plane decap

@@
 Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.
-Left:  The $r$-band Fundamental Plane from SDSS along with our GLSB galaxies and best-fit line.
+Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
@@
 We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply galaxies with similar magnitudes, colors, and redshifts to our GLSBs.
-See \citet{Saulder13} for a more rigorous analysis of the Fundamental Plane in SDSS.
+See \citet{Saulder13} for a more rigorous analysis of the fundamental plane in SDSS.
 
@@
 
-The Fundamental Plane contours in Figure~\ref{elliptical_relations} was computed from:
+The fundamental plane contours in Figure~\ref{elliptical_relations} was computed from:
 %fund_2

### 2016-01-29 glsb.tex
add new malin 1 paper
writing

@@
-\documentclass[12pt,preprint]{aastex}
-%\documentclass{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
+\documentclass{emulateapj}
 \usepackage{url}
@@
 
+\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.
+
 %\citet{Pickering97} has the \HI\ rotation curves of these guys.
@@
 
-\begin{deluxetable}{l l c c c c c c}
+\begin{deluxetable*}{l l c c c c c c}
 %\tabletypesize{\small \footnotesize \scriptsize}
@@
 \startdata
+XXX-add Malin 1
 Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  & 11.15 & 10.6\\
@@
 \tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS.}
-\end{deluxetable}
+\end{deluxetable*}
 
@@
 
-The diameters of GLSB disks are very large, with Malin~1's stellar dist detected out to a radius of 115 kpc \citep{Moore06}.
+The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 115 kpc \citep{Moore06} and 80 kpc \citep{Galaz15}.
 Stellar disks are typically embedded in much larger \HI\ disks.
@@
 While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.
-This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems without some additional source of angular momentum.
+This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems unless an interaciton is able to boost the \HI\ angular momentum.
 
@@
 THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.
 It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.
@@
 For Malin 2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).
-For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of$0.46\times 10^{11} \msun$ ).
+For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of $0.46\times 10^{11} \msun$ ).
 
@@
 This gives us 361 unique non-zero model spectra.
+XXX-cite which SED code I'm using and IMF etc.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \epsscale{0.25}
-\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps}
+\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps} \\
 \plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
@@
 \label{malin_kinem}}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \epsscale{0.25}
-\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps}
+\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps} \\
 \plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
@@
 \HI\ data from \citet{Pickering97}.\label{ugc_kinem}}
-\end{figure}
+\end{figure*}
 

### 2016-02-03 glsb.tex
ack
fixing plots and text

@@
 \citet{Pen06} find that extended disks can be formed via the disruption of dwarf galaxies.
-These simulated debrie disks have exponential profiles and extend out to 200 kpc from the central galaxy.
+These simulated debris disks have exponential profiles and extend out to 200 kpc from the central galaxy.
 
@@
 \citet{Barth07} analyze HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging.
-\citet{Barth07} points out that exteded disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).
+\citet{Barth07} points out that extended disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).
 
-If GLSB disks are indeed the remains of accreted dwarf galaxies, they represent a unique opportunity to observationally probe the outer regions of galaxy dark matter halos, especailly if they form around elliptical galaxies.
+If GLSB disks are indeed the remains of accreted dwarf galaxies, they represent a unique opportunity to observationally probe the outer regions of galaxy dark matter halos, especially if they form around elliptical galaxies.
 The mass profiles of elliptical galaxies have been difficult to constrain since they lack the extended \HI\ disks found around spirals.
-As an example of how difficult it can be to measure the outer regions of ellipical galaxy kinematics, \citet{Murphy2011} model M87 out to $\sim$23 kpc with stellar kinematics and out to 51 kpc with globular clusters (or $R=4.8 R_e$, where $R_e$ is the effective radius).
+As an example of how difficult it can be to measure the outer regions of elliptical galaxy kinematics, \citet{Murphy2011} model M87 out to $\sim$23 kpc with stellar kinematics and out to 51 kpc with globular clusters (or $R=4.8 R_e$, where $R_e$ is the effective radius).
 \citet{Raskutti14} are also limited to measuring kinematics out to $\sim$2-5 $R_e$.
@@
 \colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
-& \colhead{$\sigma$} & Stellar Mass & \colhead{\HI\ mass}\\
-     &  \colhead{(DR 9)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms}  &\colhead{log$_{10}$M$_{\odot}$}&\colhead{log$_{10}$M$_{\odot}$}
+& \colhead{$\sigma$}  & \colhead{\HI\ Mass} & \colhead{Stellar Mass} \\
+     &  \colhead{(DR 10)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms} & \colhead{log$_{10}$M$_{\odot}$} & \colhead{log$_{10}$M$_{\odot}$}
 \label{basic_prop}}    
 \startdata
-XXX-add Malin 1
-Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  & 11.15 & 10.6\\
-UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 & 10.66 & 10.5
+Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
+Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
+UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
 \enddata
-\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS.}
+\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
 \end{deluxetable*}
+
+% SDSS stellar masses.  using stellarMassFSPSGranEarlyDust:
+% Malin 2:  logMass	11.3307373297902
+% Malin 1:  logMass	11.1328074307929
+% UGC 6614: logMass	10.8745260407613
 
@@
 
-\begin{figure}
+\begin{figure*}
 \epsscale{.4}
@@
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
-Looking at the SDSS data, our GLSB galaxies appear as realtively typical red elliptical galaxies.
+Looking at the SDSS data, our GLSB galaxies appear as relatively typical red elliptical galaxies.
 \label{elliptical_relations}}
-\end{figure}
+\end{figure*}
 
@@
 While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.
-This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems unless an interaciton is able to boost the \HI\ angular momentum.
+This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems unless an interaction is able to boost the \HI\ angular momentum.
 
 %/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
-\begin{figure}
+\begin{figure*}
 \epsscale{.5}
@@
 \caption{ Comparison of the GLSB disks with other galaxy disks from the literature.
-THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.
+THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}.
 Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.
@@
 \label{disk_comp}}
-\end{figure}
+\end{figure*}
 
@@
 Figures~\ref{malin_kinem} and~\ref{ugc_kinem} show the kinemetry fits and extracted rotation curves.
-We iterate the fit, clipping residuals which deviate from the model my more than 250 \kms.
+We iterate the fit, clipping residuals which deviate from the model by more than 250 \kms.
 
@@
 This gives us 361 unique non-zero model spectra.
-XXX-cite which SED code I'm using and IMF etc.
+We use \citet{Bruzual03} with a Chabrier IMF to generate the model spectra.
 
@@
 %--now on new mac.  /Users/yoachim/Research/GLSB/THINGS/guess_projen.py
-\begin{figure}
+\begin{figure*}
 \epsscale{0.5}
@@
 \label{thingsMHI}}
-\end{figure}
+\end{figure*}
 
@@
 
+While the old stellar populations in the disks is evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
+Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is descended from a collisional ring.
+
 \section{Conclusions}
@@
 The stars have a disk-like velocity field, are dominated by old stars, but do show signs of ongoing star formation.
-The stars also show a sharp metalicity transition, consistent with the disk forming independently of the bulge.
+The stars also show a sharp metallicity transition, consistent with the disk forming independently of the bulge.
 The \HI content of the disk is also consistent with coming from a low-mass accreted galaxy.
@@
 \appendix
-\section{SDSS SQL Querries} \label{SQL}
+\section{SDSS SQL Queries} \label{SQL}
 To build our sample of comparison galaxies from SDSS, we used the CasJobs interface to query the SDSS DR10 database.
@@
 % LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA DM
-% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC
+% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC Galaz
 % LocalWords:  kpc HIPASS CCD metallicity MANGA SDSS arcsec lensing IRAF
 % LocalWords:  Spectrograph spectrograph IDL longslit photometric FWHM SSP mis
-% LocalWords:  dispersions Balmer decrement fiducia redshift
+% LocalWords:  dispersions Balmer decrement fiducia redshift Chabrier
 % LocalWords:  Faber redshifts NGC kinemetry photometry anisotropy Gyr SFH

### 2016-02-04 glsb.tex
lunch break

@@
 
-\subsection{IFU spectra}
 We obtained spatially resolved spectroscopy of our target galaxies using the Mitchell Spectrograph (formerly VIRUS-P)\citep{Hill08} on the 2.7m Harlan J.
@@
 
-\subsection{GLSB Centers}
+\subsection{GLSB Centers}\label{sec:centers}
 
@@
 %{'tau': 0.087, 'omega_n_0': 0.0, 'sigma_8': 0.809, 'h': 0.704, 'N_nu': 0, 'omega_lambda_0': 0.7274, 'n': 0.963, 'Y_He': 0.24, 'z_reion': 10.4, 'omega_b_0': 0.0456, 'omega_k_0': 0.0, 't_0': 13.75, 'omega_M_0': 0.2726}
-%xxx-clearly need to do a galfit to the central objects and show the residuals!  hmm, they are not well fit by simple Sersic profiles
 
@@
 
-The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.
+The central regions of GLSBs are often refered to in the literature as ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.
 
@@
 \end{equation}
-where $R_0$ is the effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.
+where $R_0$ is the galaxy's effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.
 The resulting best-fit parameters are  a =1.376 , b = -0.661, c = -9.938.
@@
 
-\subsection{GLSB Disks}
+\subsection{GLSB Disks}\label{sec:disks}
 
-The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 115 kpc \citep{Moore06} and 80 kpc \citep{Galaz15}.
+The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 80 kpc \citep{Galaz15}.
 Stellar disks are typically embedded in much larger \HI\ disks.
@@
 
-For comparison:  \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.
+%For comparison, \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.
 
@@
 Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.
-It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.
-\label{disk_comp}}
+These are all maximum detection radii, and thus should be considered lower limits.
+XXX--add in the stellar disks for Malin 2 and UGC 6614.
+\citet{Kasparova14} trace the light out to 60\arcsec on Malin~2, so 56 kpc\label{disk_comp}.
+I trace UGC 6614 out to 65\arcsec, so 29 kpc.}
 \end{figure*}
 
-\section{Kinematics}
+\section{Kinematics}\label{sec:kinematics}
 
@@
 
-It might be nice to spin this as a chance to measure the DM halo of ellipticals to very large radii.  Some relevant papers for comparison:
-\citet{Weij09} use SAURON to get way out.  \citet{Proctor09} use Keck.  \citet{Murphy2011} use VP.
-
-%$R_e = 7.3$\arcsec for UGC06614\\
-%$R_e = 7.17$\arcsec for Malin2
-
-The kinematics of the extended GLSB disks represents a unique probe for measuring the extended dark matter halo of elliptical galaxies.
+As we have shown in \S\ref{sec:centers} and \S\ref{sec:disks}, GLSB galaxies can be well described as large normal ellipticals that have managed to accrete a high angular momentum disk of stars and gas.
+Given the total \HI mass in GLSBs, the accreted object is consistent with a much lower-mass gas-rich spiral.
+If this is in fact the way GLSBs form, the disk kinematics represent a unique probe of the dark matter halo of elliptical galaxies.
 
@@
 
-Notes on individual rotation curves:
-The Malin 2 rotation curve is rather complicated, having several abrupt rises.
+The Malin 2 rotation curve (Figure~\ref{malin_kinem}) is rather complicated, having several abrupt rises.
 This is especially strange given the very smooth photometric profile.
-UGC 6614, on the other hand, has a relatively normal spiral galaxy-like rotation curve that rises linearly out to 10 kpc and then flattens.
+UGC 6614 (Figure~\ref{ugc_kinem}), on the other hand, has a relatively normal spiral galaxy-like rotation curve with a linear rise and flat outer region.
+One important difference is that the linear rise extends for 10 kpc.
 
 The lack of rotation in the central regions of the galaxies is not particularly surprising, as this is the region that is flux-dominated by the central elliptical galaxy.
-XXX-that hopefully we have data that shows they are not rotating or rotating in a different orientation.
 
@@
 
+Thus, using just the stellar kinematics, for Malin~2, we reach a radius of $\sim 6.2 R_e$, and find a dark matter fraction of 81\%.
+For UGC 6614, we reach a radius of  $\sim 5.2 R_e$ and find a dark matter fraction of 71\%.
+
+\citet{Murphy2011} are able to use IFU observations of M87 to reach $\sim2 R_e$ using just stellar data, and then rely on globular cluster kinematics to extended out to $5 R_e$ where they find a dark matter fraction of 85\%.
+\citet{Weij09} is similarly able to use IFU observations to reach $\sim 4 R_e$ on two elliptical galaxies while \citet{Proctor09} reaches $\sim 3 R_e$ using multi-object spectroscopy.
+
 %using /astro/store/shared-scratch1/yoachim/Research/GLSB/Analysis/mass_estm.pro
-If we use the circular speed of the \HI\ data, we end up with masses of $25\times 10^{11} \msun$ for Malin 2 and $6.5\times 10^{11} \msun$ for UGC 6614.
+If we use the circular speed of the \HI\ data from the literature, we end up with masses of $25\times 10^{11} \msun$ for Malin 2 and $6.5\times 10^{11} \msun$ for UGC 6614.
 So that's dynamical to stellar mass ratios of 18 and 14 respectively.
-Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.
+%Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.
 
-Thus, for Malin~2, we reach a radius of $\sim 6.2 R_e$, and find a dark matter fraction of 81\%.  For UGC 6614, we reach a radius of  $\sim 5.2 R_e$ and find a dark matter fraction of 71\%.
-
-\citet{Murphy2011} reach $\sim2 R_e$ using just stellar data, and then rely on globular cluster kinematics to extended out to $5 R_e$.
+%Some relevant papers for comparison:
+%\citet{Weij09} use SAURON to get way out.  \citet{Proctor09} use Keck.  \citet{Murphy2011} use VP.
+%$R_e = 7.3$\arcsec for UGC06614\\
+%$R_e = 7.17$\arcsec for Malin2
 
@@
 
-XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
+%XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
 

### 2016-02-06 glsb.tex
update plot
huh
minor fiddles

@@
 
-%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
+% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
 \begin{figure*}
@@
 \caption{ Comparison of the GLSB disks with other galaxy disks from the literature.
-THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.
+THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}, \citet{Kasparova14}, and this paper.
+Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies.
+For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars show the maximum detected stellar light radius.
 These are all maximum detection radii, and thus should be considered lower limits.
-XXX--add in the stellar disks for Malin 2 and UGC 6614.
-\citet{Kasparova14} trace the light out to 60\arcsec on Malin~2, so 56 kpc\label{disk_comp}.
-I trace UGC 6614 out to 65\arcsec, so 29 kpc.}
+\label{disk_comp}}
 \end{figure*}
@@
 
-%Some relevant papers for comparison:
-%\citet{Weij09} use SAURON to get way out.  \citet{Proctor09} use Keck.  \citet{Murphy2011} use VP.
 %$R_e = 7.3$\arcsec for UGC06614\\

### 2016-02-10 glsb.tex
quick edit
minor edits

@@
 \keywords{galaxies: kinematics and dynamics --- galaxies: formation --- galaxies: structure}
+
+\section{TO DO}
+\begin{itemize}
+\item{plug in numbers from Lauren's metallicity gradients}
+  \item{expand discussion of Kasperova14}
+\end{itemize}
 
@@
 \caption{ Comparison of the GLSB disks with other galaxy disks from the literature.
-THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}, \citet{Kasparova14}, and this paper.
-Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies.
-For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars show the maximum detected stellar light radius.
+THINGS data taken from \citet{DeBlok2008}, gLSB \HI\ data from Malin 1 from \citet{Pickering97} and gLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.
+Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.
+For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.
 These are all maximum detection radii, and thus should be considered lower limits.
@@
 \acknowledgments
-Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. 
+Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
 %Thanks to the observing specialists at Apache Point for their help executing our remote observations.

### 2016-06-01 glsb.tex
printing out
cleaning out xxx's

@@
 
-\shorttitle{Short Title}
+\shorttitle{GLSB as Merger Remnants}
 \shortauthors{Yoachim et al.}
@@
 In comparison, the stellar disk of Malin~2 extends beyond 40 kpc (5.9 $R_e$), and the HI disk reaches beyond 100 kpc (14.8 $R_e$).
+\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.
 These distances have occasionally been reached by x-ray observations \citep{Buote12}.
@@
 The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum.
-xxx-this goes in the discussion I think.
+-this goes in the discussion I think.
 \citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.
@@
 
-XXX-\citet{Kasparova14} has an amazing analysis of Malin 2.
-They combine ARC photometry, DIS spectra, and Gemini spectra to mass-model the system.
+In one of the most extensive studies of a gLSB system, \citet{Kasparova14} combine ARC 3.5m photometry and long-slit spectra with Gemini spectra to mass-model Malin~2.
 They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.
-They think the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.
-I think this is begging the question a little bit
-
-\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.
+They speculate the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.
+To some extent, this is not a particularly satisfying conclusion because one is then left with the mystery of why Malin~2's dark matter halo is so different from non-giant galaxies.
 
@@
 
-%XXX-need to look up some Thilker papers on extended UV disks, since these objects could be similar.
+%-need to look up some Thilker papers on extended UV disks, since these objects could be similar.
 From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).
@@
 Malin 2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.
-Both galaxies were observed with the XXX gratings and multiple positions of the 1.5\arcsec\ slit.
-%XXX-insert table with galaxy name, position, total exposure time
-%XXX-insert figure showing slit positions overlayed on the SDSS thumbnails.
+Both galaxies were observed with the  gratings and multiple positions of the 1.5\arcsec\ slit.
+%-insert table with galaxy name, position, total exposure time
+%-insert figure showing slit positions overlayed on the SDSS thumbnails.
 
@@
 
-%XXX-crap, whatever happened to the gas kinematics?
+%-crap, whatever happened to the gas kinematics?
 There are emission lines out there--are they bright enough to get in single fibers of not?
@@
 
-%XXX-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
-
-XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
+%-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
 
@@
 
-XXX-clearly need to look up bulge-to-disk metallicity gradient.
-Lauren did it with colors in \citet{MacArthur04}.
-Nice look with metallicity gradients as a function of scale-length, and kpc, and vrot and galaxy type.
-Did spectra gradients in \citet{MacArthur09}.
-MANGA would make this easy to compare...Maybe there's a SAURON paper on metallicity gradients.
+One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).
+For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.
+This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.
+\citet{MacArthur04} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
+Using braidband colors, \citet{MacArthur04} also found metallicity gradients of $\sim0$\ to $-0.1$ dex kpc$^{-1}$, at least a factor of two less than what we observe in Malin~2.
+Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.
 
-While the old stellar populations in the disks is evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
-Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is descended from a collisional ring.
+While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
+Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.
 
@@
 
-In a future work, we plan to combine our IFU observations with higher spatial resolution long-slit spectra from the Apache Point 3.5m telescope to determine if the central ellipticals are dynamically distinct from their disks.
+We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
 
@@
 %\end{figure}
-%XXX-do an actual tilted ring fit to this shit.
+%do an actual tilted ring fit to this shit.
 
@@
 For all radial bins, the stellar mass is dominated by stars older than 2 Gyr.
-Error bars represent the best XXX fitting models.
+Error bars represent the best fitting models.
 \label{sfh_ugc} }

### 2016-06-01 glsb.tex
fiddle

@@
 
-We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.
+We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.
 
@@
 It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.
+While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
+Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.
 
@@
 Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.
-
-While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
-Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.
 

### 2016-06-03 glsb.tex
working on discussion

--- 2016-06-01 glsb.tex
@@
 \keywords{galaxies: kinematics and dynamics --- galaxies: formation --- galaxies: structure}
-
-\section{TO DO}
-\begin{itemize}
-\item{plug in numbers from Lauren's metallicity gradients}
-  \item{expand discussion of Kasperova14}
-\end{itemize}
 
@@
 
-We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.
+We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin~1 \citep{Barth07} and NGC~7589 \citep{Lelli10}.
 
@@
 It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.
-
-Accretion can also form GLSB systems around any type of host galaxy, explaining how \citet{Barth07} can find that Malin~1 is an SB0 galaxy, while our two systems are normal ellipticals.
-
-%Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.
-We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.
-
-If these systems do prove to be ellipticals with accreted high angular momentum disks, they represent an amazing opportunity to probe the dark matter halo properties of elliptical systems to very large radii.
+While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
+Since photometric surveys are often surface brightness limited, it is possible a GLSB system will be found in the future that is the decendent of a collisional ring system.
 
@@
 This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.
-\citet{MacArthur04} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
-Using braidband colors, \citet{MacArthur04} also found metallicity gradients of $\sim0$\ to $-0.1$ dex kpc$^{-1}$, at least a factor of two less than what we observe in Malin~2.
+\citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
+Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies.
 Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.
 
-While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
-Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.
+\citet{Kasparova14} present one of the most in depth observational studies of Malin~2.
+Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc.
+\citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.
+It is probably foolish to directly compare gas and stellar metallicities, but it is interesting that the gas metallicity gradient appears to be much lower than the stellar gradient.
+This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be heklpful in confirming what the final expected gas metallicity gradient should be.
+
+If these systems do prove to be ellipticals with accreted high angular momentum disks, they represent an amazing opportunity to probe the dark matter halo properties of elliptical systems to very large radii.
 
@@
 \acknowledgments
-Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
+Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs.
+Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
+Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
 %Thanks to the observing specialists at Apache Point for their help executing our remote observations.

### 2016-07-11 glsb.tex
add califa paper
add more discussion

@@
 Individual science exposures were 30 minutes.
-Malin 2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.
+Malin~2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.
 Observations of UGC 06614 had alignment issues between observing runs.
@@
 
-Outline for discussion section
-\begin{itemize}
-\item{We find the GLSB systems Malin~2 and UGC~6614 are observationally most consistent with being normal elliptical galaxies that have undergone a high angular momentum minor merger with a gas rich system.}
-\item{recap photometric evidence--the centers look just like SDSS ellipticals.}
-\item{recap star formation histories. Disk is dominated by old stars.}
-\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.
-      \citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
-Lots of good stuff on fast/slow rotators.
-Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.
-They don't see any sharp transition like I do, all very smooth age and metal curves.
-}
-\item{extended comparison to \citet{Kasparova14}}
-  \begin{itemize}
-    \item{Mass model of Malin~2 requires a huge isothermal core radius.}
-    \item{They measure gas metallicities and find solar in the center and half-solar at 20-30 kpc.
-While it is a fool's errand to compare metallicities between stars and gas, it is interesting that the gas metallicity gradient is much smaller than in the stars.
-If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.
-Hmm, looking at DR12 stuff, the pipeline reductions are fitting solar metallicity to the center, not sure I believe that.
-}
-      \item{They have a nice mass-model that becomes dark matter dominated at around r=20 kpc.  Could this be the normal shape of elliptical dark matter halos?}
-  \end{itemize}
-
-\item{This could be the strongest evidence for very massive elliptical dark matter halos. }
-  \item{plan on getting higher spatial resolution spectra of the centers to confirm they are typical elliptical galaxies.}
-\end{itemize}
+XXX-organize this up a little more.
 
@@
 An accretion formation scenario does the best job explaining all the observations.
-While a collisional ring could fade to a GLSB, the stellar population should be relatively young, and one might not expect a steep metallicity gradient.
+While a collisional ring could fade to a GLSB, the stellar population should be relatively young, and one would not necissarily expect a steep metallicity gradient.
 Also, there are no obvious galaxies near GLSBs to act as progenitor colliders.
@@
 While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.
-Since photometric surveys are often surface brightness limited, it is possible a GLSB system will be found in the future that is the decendent of a collisional ring system.
-
-Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.
-Also see \citet{Capp11} that says slow rotators are very rare in the field.
-So it might be strange if Malin 2 and UGC 6614 are slow rotators.
+Since photometric surveys are often surface brightness limited, it is possible a GLSB system will be found in the future that is the descendant of a collisional ring system.
 
@@
 
+\citet{Sanchez14} measure the Oxygen abundance from gas emission lines in a large sample of spiral galaxies and find a characteristic slope of $\alpha_{\rm{O/H}} = -0.1$\ dex $r_e^{-1}$ between 0.3 and 2 effective radii.
+The metallicity gradients we observe in Malin~2 and UGC~6614 are factors of 2-4 steeper than the typical spiral.
+Also, of the 193 galaxies in \citet{Sanchez14} only four have a slope steeper than -0.3 \ dex $r_e^{-1}$ \citep[Figure~6]{Sanchez14}.
+In their Figure~9, they combine the data to show a typical gas metallicity curve that drops linearly until $r_e\sim2$ and then flattens to a constant value.
+This shape is very different from the step function change we observe in the GLSBs.
+
+% malin 2: R_e = 7.17"
+% UGC : 7.3"
+
 \citet{Kasparova14} present one of the most in depth observational studies of Malin~2.
@@
 It is probably foolish to directly compare gas and stellar metallicities, but it is interesting that the gas metallicity gradient appears to be much lower than the stellar gradient.
-This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be heklpful in confirming what the final expected gas metallicity gradient should be.
+This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be helpful in confirming what the final expected gas metallicity gradient should be.
 
@@
 
+Outline for discussion section
+\begin{itemize}
+\item{We find the GLSB systems Malin~2 and UGC~6614 are observationally most consistent with being normal elliptical galaxies that have undergone a high angular momentum minor merger with a gas rich system.}
+\item{recap photometric evidence--the centers look just like SDSS ellipticals.}
+\item{recap star formation histories. Disk is dominated by old stars.}
+\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.
+      \citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
+Lots of good stuff on fast/slow rotators.
+Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.
+They don't see any sharp transition like I do, all very smooth age and metal curves.
+}
+\item{extended comparison to \citet{Kasparova14}}
+  \begin{itemize}
+    \item{Mass model of Malin~2 requires a huge isothermal core radius.}
+    \item{They measure gas metallicities and find solar in the center and half-solar at 20-30 kpc.
+While it is a fool's errand to compare metallicities between stars and gas, it is interesting that the gas metallicity gradient is much smaller than in the stars.
+If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.
+Hmm, looking at DR12 stuff, the pipeline reductions are fitting solar metallicity to the center, not sure I believe that.
+}
+      \item{They have a nice mass-model that becomes dark matter dominated at around r=20 kpc.  Could this be the normal shape of elliptical dark matter halos?}
+  \end{itemize}
+
+\item{This could be the strongest evidence for very massive elliptical dark matter halos. }
+  \item{plan on getting higher spatial resolution spectra of the centers to confirm they are typical elliptical galaxies.}
+\end{itemize}
+
+Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.
+Also see \citet{Capp11} that says slow rotators are very rare in the field.
+So it might be strange if Malin 2 and UGC 6614 are slow rotators.
+
 % LocalWords:  Debattista Horrocks Lancashire RCUK Malin Stanonik Spavone Lelli

### 2016-07-27 glsb.tex
add ref
edits

@@
 Seattle WA, 98195}
-\altaffiltext{2}{XXX-U Mich}
+\altaffiltext{2}{University of Michigan}
 \altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}
-\altaffiltext{4}{XXX-Cal Tech}
+\altaffiltext{4}{California Institute of Technology}
 
@@
 We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.
-We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone a high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
+We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
 We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.
@@
 Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.
-Even the Galaxy Zoo project classifies GLSB galaxies as spirals.
+Even the Galaxy Zoo project \citep{Willett13}  classifies GLSB galaxies as spirals.
 While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.
@@
 In their model, a collision sets off an expanding ring of star formation.
-As this the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.
+As the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.
 One obvious problem with this scenario is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.
 
-The another formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
+The other popular formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
 \citet{Pen06} find that extended disks can be formed via the disruption of dwarf galaxies.
@@
 In comparison, the stellar disk of Malin~2 extends beyond 40 kpc (5.9 $R_e$), and the HI disk reaches beyond 100 kpc (14.8 $R_e$).
-\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.
-These distances have occasionally been reached by x-ray observations \citep{Buote12}.
+\citet{Galaz15} take deep images of Malin~1 and find the stellar disk diameter extends to 160 kpc.
+
+%These distances have occasionally been reached by x-ray observations of giant elliptical galaxies \citep{Buote12}.
 
@@
 
-In one of the most extensive studies of a gLSB system, \citet{Kasparova14} combine ARC 3.5m photometry and long-slit spectra with Gemini spectra to mass-model Malin~2.
-They find the broadband colors are not consistent with a catastrophic formation, but are best fit by exponentially declining SFH.
+In one of the most extensive studies of a GLSB system, \citet{Kasparova14} combine ARC 3.5m photometry and long-slit spectra with Gemini spectra to mass-model Malin~2.
+They find the broadband colors of the extended disk are not consistent with a catastrophic formation, but are best fit by an exponentially declining SFH.
 They speculate the main difference between Malin~2 and non-giant LSB galaxies is the dark matter halo scale.
 To some extent, this is not a particularly satisfying conclusion because one is then left with the mystery of why Malin~2's dark matter halo is so different from non-giant galaxies.
+
+XXX-in this paper we blah dee blah. In \S\ref{sec:obs} blah blah.
 
@@
 
-\section{Observations}
+\section{Observations}\label{sec:obs}
 
@@
 This resulted in a deep stack of 6 exposures, and a shallow stack with only 2 exposures.
-With only 2 exposures, cosmic ray rejection becomes difficult, therefore, we use these shallow frames when looking at the surface brightness profiles, but use only the aligned deep co-add when analyzing the stellar kinematics and stellar populations.
+With only 2 exposures, cosmic ray rejection becomes unreliable, therefore, we use these shallow frames when looking at the surface brightness profiles, but use only the aligned deep co-add when analyzing the stellar kinematics and stellar populations.
 Twilight flat field frames, bias frames, and wavelength calibration Hg and Cd lamps were taken during the day.
@@
 We use the b-spline procedure described in \citet{Kelson03} to generate background frames.
-The corners contain enough empty fibers to measure the sky background in each exposure.
+The corners of the IFU array contain enough empty fibers to measure the sky background in each exposure.
 Because we bin fibers together, imperfect sky-subtraction represents a serious source of potential systematic errors.
@@
 By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.
-In the SDSS DR10 \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.
+In the Sloan Digital Sky Survey Data Relase 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.
 In this section, we compare the properties of the GLSB centers and disks with other systems.
@@
 
-Both of our objects, as well as Malin 1, have been observed with SDSS, making it possible to compare them to a large number of systems.
+Both of our objects, as well as Malin~1, have been observed with SDSS, making it possible to compare them to a large number of systems.
 The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.
@@
 To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddened $r$ magnitude between 13.5 and 17.7.
-When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology selectors).
+When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology cuts).
 These are simply galaxies for comparison, not a rigorously defined volume-complete sample.
@@
 \caption{
-Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin 2 and UGC 6614.
+Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin~2 and UGC~6614.
 Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.
@@
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
-Looking at the SDSS data, our GLSB galaxies appear as relatively typical red elliptical galaxies.
+From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively normal red elliptical galaxies.
 \label{elliptical_relations}}
@@
 where $R_0$ is the galaxy's effective radius, $\sigma$ is velocity dispersion in kilometers per second and $I_0$ is the surface brightness.
-The resulting best-fit parameters are  a =1.376 , b = -0.661, c = -9.938.
-We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply galaxies with similar magnitudes, colors, and redshifts to our GLSBs.
+The resulting best-fit parameters are  $a =1.376$ , $b = -0.661$, $c = -9.938$.
+We note that we have not made a rigorous volume-complete selection of galaxies, rather, simply selected galaxies with similar magnitudes, colors, and redshifts to our GLSBs.
 See \citet{Saulder13} for a more rigorous analysis of the fundamental plane in SDSS.
@@
 
-The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 80 kpc \citep{Galaz15}.
-Stellar disks are typically embedded in much larger \HI\ disks.
-The size of the GLSB stellar disks is similar to the largest \HI\ disks observed in nearby galaxies, in support of the \citet{Mapelli08} model where the GLSB disks are the faded remnants of a normal \HI\ disk that has experienced a merger induced star-burst.
+XXX--do find-replace check for Malin 2 and UGC 6614 to Malin~2 and UGC~6614
 
@@
 
-In Figure~\ref{disk_comp}, we compare the sizes of the stellar disks of the GLSB galaxies with other observations.
+The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 80 kpc \citep{Galaz15}.
+Stellar disks are typically embedded in much larger \HI\ disks.
+In Figure~\ref{disk_comp}, we compare the sizes of the stellar and \HI\ disks of the GLSB galaxies with other observations.
 For this plot, we take the maximum detected radius from the literature for the galaxies.
 It is possible that deeper observations could increase the values of $R_{max}$.
-While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.
-This seems to point against the GLSB formation mechanism of \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems unless an interaction is able to boost the \HI\ angular momentum.
+While the stellar disk of UGC~6614 is close in size to local observed \HI\ disks, Malin~1 and~2 are larger than hte \HI\ disks observed in the THINGS survey.
+This seems to point against the GLSB formation mechanism of \citet{Mapelli08}, as we do not observe \HI\ disks in normal spirals large enough to convert into GLSB systems unless an interaction is able to also boost the angular momentum of the resulting stellar disk.
 
@@
 \caption{ Comparison of the GLSB disks with other galaxy disks from the literature.
-THINGS data taken from \citet{DeBlok2008}, gLSB \HI\ data from Malin 1 from \citet{Pickering97} and gLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.
+THINGS data taken from \citet{DeBlok2008}, GLSB \HI\ data from Malin 1 from \citet{Pickering97} and GLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.
 Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.
-For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.
-These are all maximum detection radii, and thus should be considered lower limits.
+For the GLSB galaxies, the solid points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.
+All points are maximum detection radii, and thus should be considered lower limits.
 \label{disk_comp}}
@@
 As we have shown in \S\ref{sec:centers} and \S\ref{sec:disks}, GLSB galaxies can be well described as large normal ellipticals that have managed to accrete a high angular momentum disk of stars and gas.
-Given the total \HI mass in GLSBs, the accreted object is consistent with a much lower-mass gas-rich spiral.
+Given the total \HI\ mass in GLSBs, the accreted object is consistent with a much lower-mass gas-rich spiral.
 If this is in fact the way GLSBs form, the disk kinematics represent a unique probe of the dark matter halo of elliptical galaxies.
@@
 
-The Malin 2 rotation curve (Figure~\ref{malin_kinem}) is rather complicated, having several abrupt rises.
+The Malin~2 rotation curve (Figure~\ref{malin_kinem}) is rather complicated, having several abrupt rises.
 This is especially strange given the very smooth photometric profile.
-UGC 6614 (Figure~\ref{ugc_kinem}), on the other hand, has a relatively normal spiral galaxy-like rotation curve with a linear rise and flat outer region.
+UGC~6614 (Figure~\ref{ugc_kinem}), on the other hand, has a relatively normal spiral galaxy-like rotation curve with a linear rise and flat outer region.
 One important difference is that the linear rise extends for 10 kpc.
@@
 Other cites for elliptical gradients \citep{Kuntschner10}
+
+\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallitcity gradients for late type galaxies.
 
@@
 
+\citet{Hagen16} present the discovery of a GLSB system around UGC~1382.
+As in this work, they find the best explination of the extended disk as being the remnants of an accreted drawf galaxy similar to the simulations of \citet{Pen06}.
+
 If these systems do prove to be ellipticals with accreted high angular momentum disks, they represent an amazing opportunity to probe the dark matter halo properties of elliptical systems to very large radii.
@@
 \plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
-\caption{Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.
+\caption{XXX--break this into 2 figures!
+Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.
 The dashed curve shows the expected stellar mass contribution to the rotation curve.
@@
 \plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
-\caption{Fitting the velocity maps with kinemetry package.
+\caption{XXX-break into 2 figures!
+Fitting the velocity maps with kinemetry package.
 Vertical lines mark $R_e$ and $5R_e$.

### 2016-07-28 glsb.tex
edits

@@
 This is especially strange given the very smooth photometric profile.
-UGC~6614 (Figure~\ref{ugc_kinem}), on the other hand, has a relatively normal spiral galaxy-like rotation curve with a linear rise and flat outer region.
+UGC~6614 (Figure~\ref{ugc_kinem}), on the other hand, has a typical late-type galaxy rotation curve with a linear rise and flat outer region.
 One important difference is that the linear rise extends for 10 kpc.
@@
 %using /astro/store/shared-scratch1/yoachim/Research/GLSB/Analysis/mass_estm.pro
-If we use the circular speed of the \HI\ data from the literature, we end up with masses of $25\times 10^{11} \msun$ for Malin 2 and $6.5\times 10^{11} \msun$ for UGC 6614.
-So that's dynamical to stellar mass ratios of 18 and 14 respectively.
+If we use the circular speed of the \HI\ data from the literature, we end up with dynamical masses of $25\times 10^{11} \msun$ for Malin~2 and $6.5\times 10^{11} \msun$ for UGC~6614 (dynamical to stellar mass ratios of 18 and 14 respectively).
 %Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.
@@
 We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.
-Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.
-We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.
+Each SFH can have a metallicity of [Z/H] = -2.3, -1.70, -0.70, -0.40, 0.0, or 0.40.
+We do not include any metallicity evolution, as all the age bins in a given model have the same metallicity.
 This gives us 361 unique non-zero model spectra.
@@
 Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
+We find the best-fitting single model spetrum for each observed binned spectrum.
+When fitting, we include a low order multiplicitave polynomial to match any dust extinction or flux calibration errors in the observations.
+This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as 10 M$_\sun$ yr$^{-1}$.)
 
@@
 We find that {\emph{both galaxies have stellar populations dominated by old stars at all radii}}.
-While the outer disks have emission lines and have spectra that are best fit with some current star formation, the total stellar mass is still overwhelmingly dominated by old stars.
+While the outer disks show emission lines and are best fit with some current star formation, the total stellar mass is still overwhelmingly dominated by old stars.
 Both galaxies also show very steep metallicity gradients, with centers that are super-solar metallicity (at the limit of our models), while the outer disks are both best fit by [Z/H]=-0.7.
@@
 
-The dominance of an old stellar population at large radii seems to contradict the star-burst formation mechanism of \citet{Mapelli08}, and favor an accretion model where a galaxy already containing old stars is disrupted by a massive elliptical galaxy.
+The dominance of an old stellar population at large radii seems to contradict the star-burst formation mechanism of \citet{Mapelli08}, and favor an accretion model where a galaxy already containing old stars is disrupted by a massive elliptical galaxy similar to \citet{Pen06}.
 
-These are incredibly steep metallicity gradients.
-The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin 2 and $\sim -0.68$ for UGC 6614.
-These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
-Other cites for elliptical gradients \citep{Kuntschner10}
+%\section{Disk Progenitors}
 
-\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallitcity gradients for late type galaxies.
-
-\section{Disk Progenitors}
-
-It should be relatively easy to speculate about the galaxies that merged to form the disk.
+%It should be relatively easy to speculate about the galaxies that merged to form the disk.
 I can pull \HI\ masses, and then calc some stellar masses given the SDSS photometry and my own stellar M/L ratios.
@@
 
-Figure~\ref{thingsMHI} shows the total \HI\ mass for galaxies observed in the THINGS survey \citep{Walter2008}, along with the \HI\ masses for GLSB galaxies \citep{Pickering97}.
+%Figure~\ref{thingsMHI} shows the total \HI\ mass for galaxies observed in the THINGS survey \citep{Walter2008}, along with the \HI\ masses for GLSB galaxies \citep{Pickering97}.
 
-We can't really use the stellar luminosity of the disk to constrain the progenitor since there are signs of current {\emph in situ} star formation in the disks.
+%We can't really use the stellar luminosity of the disk to constrain the progenitor since there are signs of current {\emph in situ} star formation in the disks.
 However, the very low stellar metallicities point to low-mass progenitors.
 
-Hard to estimate what the progenitor system of the disks were.
+%Hard to estimate what the progenitor system of the disks were.
 Is there a good plot of disk \HI\ mass and metallicity out there?
@@
 
-These systems are rare enough, that one might imagine rather complicated scenarios for creating them.
+%These systems are rare enough, that one might imagine rather complicated scenarios for creating them.
 For example, a three-body encounter could eject one galaxy while leaving a second in a nearly circular orbit.
@@
 
+\section{Discussion}
+
 The basic observational properties of GLSBs that need to be explained:
 \begin{enumerate}
-\item{These galaxies have \HI\ disks that extend much farther than typical spiral galaxies (Figure~\ref{disk_comp}). }
-\item{While GLSBs have large disks, the total \HI\ mass in these disks is lower than expected given their rotational velocities (Figure~\ref{thingsMHI})}
-\item{The central bulges are similar to elliptical galaxies in SDSS (Figure~\ref{elliptical_relations}).}
-\item{The stellar populations in the centers of GLSBs are old and very metal-rich.}
-\item{The stellar populations in the extended disks shows some signs of ongoing star formation, but is consistent with being dominated by an old metal-poor population.}
+\item{\HI\ disks that extend much farther than typical spiral galaxies (Figure~\ref{disk_comp}). }
+\item{Total \HI\ masses that are lower than expected given their rotational velocities (Figure~\ref{thingsMHI}).}
+\item{Central bulges that are similar to massive elliptical galaxies in SDSS (Figure~\ref{elliptical_relations}).}
+\item{Central stellar populations that are old and very metal-rich.}
+\item{Disk stellar populations that show signs of ongoing star formation, but are dominated by an old metal-poor population.}
+\item{A sharp metallicity transition between the central bulge and disk components.}
 \end{enumerate}
@@
 \end{figure*}
-
-\section{Discussion}
-
-XXX-organize this up a little more.
 
@@
 Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies.
-Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.
+Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7).
+We have also spatially binned data, possibly washing out how sharp the transition is between bulge and disk.
 
@@
 This shape is very different from the step function change we observe in the GLSBs.
+
+These are incredibly steep metallicity gradients.
+The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin 2 and $\sim -0.68$ for UGC 6614.
+These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
+Other cites for elliptical gradients \citep{Kuntschner10}
+
+\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallitcity gradients for late type galaxies.
 
@@
 \caption{Upper Left:  SDSS image of Malin 2.
-Upper Right:  Image made with the VIRUS-P datacube.
+Upper Right:  Image made with the VIRUS-P datacube synthetic fiber magnitudes.
 Lower:  An exponential fit to the fiber magnitudes.
@@
 \epsscale{1}
+%\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
+\caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into tripples.
+Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
+Middle:  Best fitting tilted ring model from kinemetry \citet{Krajn06}.
+Right: Best fit residuals.
+\label{malin_kinem_fibers}}
+\end{figure*}
+
+\begin{figure*}
+\epsscale{0.25}
+%\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps} \\
+%\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
+%\epsscale{.5}
+\epsscale{1}
 \plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
-\caption{XXX--break this into 2 figures!
-Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.
+\caption{Rotation curves extracted from the best fitting model in Fig~\ref{malin_kinem_fibers}.
 The dashed curve shows the expected stellar mass contribution to the rotation curve.

### 2016-07-29 glsb.tex
edits

@@
 By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.
-In the Sloan Digital Sky Survey Data Relase 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.
+In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.
 In this section, we compare the properties of the GLSB centers and disks with other systems.
@@
 
-The central regions of GLSBs are often refered to in the literature as ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.
+The central regions of GLSBs are often referred to in the literature as ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.
 
@@
 It is possible that deeper observations could increase the values of $R_{max}$.
-While the stellar disk of UGC~6614 is close in size to local observed \HI\ disks, Malin~1 and~2 are larger than hte \HI\ disks observed in the THINGS survey.
+While the stellar disk of UGC~6614 is close in size to local observed \HI\ disks, Malin~1 and~2 are larger than the \HI\ disks observed in the THINGS survey.
 This seems to point against the GLSB formation mechanism of \citet{Mapelli08}, as we do not observe \HI\ disks in normal spirals large enough to convert into GLSB systems unless an interaction is able to also boost the angular momentum of the resulting stellar disk.
@@
 Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.
-For the GLSB galaxies, the solid points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.
+For the GLSB galaxies, the circular points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.
 All points are maximum detection radii, and thus should be considered lower limits.
@@
 Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
-We find the best-fitting single model spetrum for each observed binned spectrum.
-When fitting, we include a low order multiplicitave polynomial to match any dust extinction or flux calibration errors in the observations.
+We find the best-fitting single model spectrum for each observed binned spectrum.
+When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.
 This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as 10 M$_\sun$ yr$^{-1}$.)
@@
 An accretion formation scenario does the best job explaining all the observations.
-While a collisional ring could fade to a GLSB, the stellar population should be relatively young, and one would not necissarily expect a steep metallicity gradient.
+While a collisional ring could fade to a GLSB, the stellar population should be relatively young, and one would not necessarily expect a steep metallicity gradient.
 Also, there are no obvious galaxies near GLSBs to act as progenitor colliders.
@@
 
-\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallitcity gradients for late type galaxies.
+\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.
 
@@
 \citet{Hagen16} present the discovery of a GLSB system around UGC~1382.
-As in this work, they find the best explination of the extended disk as being the remnants of an accreted drawf galaxy similar to the simulations of \citet{Pen06}.
+As in this work, they find the best explanation of the extended disk as being the remnants of an accreted dwarf galaxy similar to the simulations of \citet{Pen06}.
 
@@
 We find the inner bulge is similar to elliptical galaxies found in SDSS.
-The stars have a disk-like velocity field, are dominated by old stars, but do show signs of ongoing star formation.
+The extended galaxy stars have disk-like velocity fields, are dominated by old stars, but do show signs of ongoing star formation.
 The stars also show a sharp metallicity transition, consistent with the disk forming independently of the bulge.
-The \HI content of the disk is also consistent with coming from a low-mass accreted galaxy.
+The \HI\ mass of the disk is also consistent with coming from a low-mass accreted galaxy.
 
-We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
+We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and constrain a more sophisticated dynamical model of the system.
 
@@
 Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs.
-Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
+Thanks to Dmitry Bizyaev for stimulating conversations about GLSBs.
 Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
@@
 %\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
-\caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into tripples.
+\caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into triples.
 Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
@@
 \plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
-\caption{Rotation curves extracted from the best fitting model in Fig~\ref{malin_kinem_fibers}.
-The dashed curve shows the expected stellar mass contribution to the rotation curve.
+\caption{Rotation curves extracted from the best fitting models in Fig~\ref{malin_kinem_fibers}.
+The dashed curves show the expected stellar mass contribution to the rotation curve.
 Vertical lines mark $R_e$ and $5R_e$.
@@
 \plottwo{Plots/Malin2bin_map.eps}{Plots/Malin2binned_spec.eps}
-\caption{Left:  Map of which fibers were binned together.  Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked. \label{malin2_binmap}}
+\caption{Left:  Map of which fibers were binned together for star formation history measurements.
+Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
+The inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines.
+\label{malin2_binmap}}
 \end{figure}
@@
 Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.
+The oldest age bin dominates at all radii.
 \label{sfh_malin2} }
@@
 \caption{Best fitting stellar metallicities.
-Dashed line shows the maximum model metallicity used in the models (minimum is below the y range).
+Dashed line shows the maximum model metallicity used in the models (minimum is below the y range limit).
 Error bars are as in Figure~\ref{sfh_malin2}.
@@
 \plottwo{Plots/UGC06614bin_map.eps}{Plots/UGC06614binned_spec.eps}
-\caption{Left:  Map showing which fibers were binned for UGC 6614.  Right:  The binned spectra, color-coded to match the map on the left. \label{ugc_binmap}}
+\caption{Left:  Map showing which fibers were binned for UGC 6614.
+Right:  The binned spectra, color-coded to match the map on the left.
+As with Malin~2, the inner spectra show strong metallicity absorption features while the outer spectra show emission lines.
+\label{ugc_binmap}}
 \end{figure}
@@
 \plotone{Plots/UGC06614_chibar_sfr.eps}
-\caption{ Best fitting star formation histories.
+\caption{Best fitting star formation histories.
 For each bin, the SFH is normalized by the peak bin.
 Error bars are based on $\Delta\chi^2=100$ or the 4 best fitting models, whichever provides more points.
+As with Malin~2, old stars dominate at all radii.
 \label{sfh_ugc} }
@@
 \epsscale{1}
-\caption{Best fitting stellar metallicities.   \label{metal_ugc}}
+\caption{Best fitting stellar metallicities for the binned UGC~6614 spectra.  Dashed line shows the maximum model value.  \label{metal_ugc}}
 \end{figure}
@@
 \plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
-%\epsscale{.5}
+\epsscale{1}
+\caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into triples.
+Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
+Middle:  Best fitting tilted ring model from kinemetry \citet{Krajn06}.
+Right: Best fit residuals.
+\label{ugc_kinem_fibers}}
+\end{figure*}
+
+\begin{figure*}
 \epsscale{1}
 \plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
-\caption{XXX-break into 2 figures!
-Fitting the velocity maps with kinemetry package.
+\caption{Rotation curves extracted from the best fitting model in Fig~\ref{ugc_kinem_fibers}.
+The dashed curve shows the expected stellar mass contribution to the rotation curve.
 Vertical lines mark $R_e$ and $5R_e$.
-The dashed lines shows a rotation curve based in the enclosed flux, normalized so that all the SDSS stellar mass is contained within $3R_e$.
-\HI\ data from \citet{Pickering97}.\label{ugc_kinem}}
+\HI\ data from \citet{Pickering97}.
+\label{ugc_kinem}}
 \end{figure*}
@@
 % LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA DM
-% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC Galaz
+% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC Galaz Myr
 % LocalWords:  kpc HIPASS CCD metallicity MANGA SDSS arcsec lensing IRAF
@@
 %%  LocalWords:  Krajn GN Kuntschner situ indices Emsell Capp CasJobs
-%%  LocalWords:  Schmitz circ accrete jabref CMD
+%%  LocalWords:  Schmitz circ accrete jabref CMD collisional GLSB's
+%%  LocalWords:  impactor Conroy brightnesses Malmquist dex Hagen
+%%  LocalWords:  Dmitry isothermal

### 2016-08-01 glsb.tex
edit

@@
 
-XXX-in this paper we blah dee blah. In \S\ref{sec:obs} blah blah.
+In \S\ref{sec:obs} we present new observations of Malin~2 and UGC~6614.
+In \S\ref{sec:compare_gals}, we compare the general properties of GLSB galaxies to sample of galaxies drawn from SDSS and the THINGS survey.
+In \S\ref{sec:kinematics} and \S\ref{sec:sfh} we measure the stellar kinematics and star formation histories from our spectra.
+In \S\ref{sec:discussion}, we discuss what our observations imply for the possible formation mechanisms for GLSB systems.
 
 %\citet{Pickering97} has the \HI\ rotation curves of these guys.
-For UGC 6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.
-And $3.6 \pm 0.4 \times 10^{10} \msun h_{75}^{-2}$for Malin 2.
+For UGC~6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.
+And $3.6 \pm 0.4 \times 10^{10} \msun h_{75}^{-2}$for Malin~2.
 Notes that these are galaxies that are massive and DM dominated.
-In Malin 2, they find some gas moving relative to the regular rotating disk, and suspect that a dwarf fell though and stimulated star formation and this could be how stars managed to form in the low density environment.
+In Malin~2, they find some gas moving relative to the regular rotating disk, and suspect that a dwarf fell though and stimulated star formation and this could be how stars managed to form in the low density environment.
 
@@
 %F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
-%UGC 6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
+%UGC~6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
 %\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.
@@
 
-%\citet{Das10} find CO in Malin 2.  Make some points about it being stable
+%\citet{Das10} find CO in Malin~2.  Make some points about it being stable
 
@@
 Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
-Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
+Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
 UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
@@
 % SDSS stellar masses.  using stellarMassFSPSGranEarlyDust:
-% Malin 2:  logMass	11.3307373297902
+% Malin~2:  logMass	11.3307373297902
 % Malin 1:  logMass	11.1328074307929
-% UGC 6614: logMass	10.8745260407613
+% UGC~6614: logMass	10.8745260407613
 
@@
 % D = c(z+0.5(1.0-q_0)z^2)/H_0
-% int(S) = 4.4 Jy km/s for Malin 2
-%        = 15.0 for UGC 6614
+% int(S) = 4.4 Jy km/s for Malin~2
+%        = 15.0 for UGC~6614
 % cosmolopy using h = 0.704.  
@@
 \startdata
-Malin 2 & 6.1 & 35.5  \\
+Malin~2 & 6.1 & 35.5  \\
 UGC 06614 & 5.7 & 33.4
@@
 %the ARC 3.5 meter telescope at Apache Point Observatory (APO).
-Malin 2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.
+Malin~2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.
 Both galaxies were observed with the  gratings and multiple positions of the 1.5\arcsec\ slit.
@@
 
-\section{Comparisons to Other Galaxies}
+\section{Comparisons to Other Galaxies}\label{sec:compare_gals}
 
 By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.
-In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC 6614.
+In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC~6614.
 In this section, we compare the properties of the GLSB centers and disks with other systems.
@@
 \subsection{GLSB Disks}\label{sec:disks}
-
-XXX--do find-replace check for Malin 2 and UGC 6614 to Malin~2 and UGC~6614
 
@@
 The extracted rotation curves imply large dark matter halos.
-For Malin 2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).
-For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of $0.46\times 10^{11} \msun$ ).
+For Malin~2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).
+For UGC~6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of $0.46\times 10^{11} \msun$ ).
 
 Thus, using just the stellar kinematics, for Malin~2, we reach a radius of $\sim 6.2 R_e$, and find a dark matter fraction of 81\%.
-For UGC 6614, we reach a radius of  $\sim 5.2 R_e$ and find a dark matter fraction of 71\%.
+For UGC~6614, we reach a radius of  $\sim 5.2 R_e$ and find a dark matter fraction of 71\%.
 
@@
 There are emission lines out there--are they bright enough to get in single fibers of not?
-Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.
-UGC 6614 is mostly emission from the center.
+Looks like for Malin~2 the emission lines are only coming from one side of the galaxy.
+UGC~6614 is mostly emission from the center.
 
@@
 
-\section{Star Formation Histories}
+\section{Star Formation Histories}\label{sec:sfh}
 
@@
 
-Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin 2 and UGC 06614.
+Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin~2 and UGC 06614.
 Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
@@
 These are incredibly steep metallicity gradients.
-The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin 2 and $\sim -0.68$ for UGC 6614.
+The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin~2 and $\sim -0.68$ for UGC~6614.
 These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
@@
 
-% malin 2: R_e = 7.17"
+% Malin~2: R_e = 7.17"
 % UGC : 7.3"
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
@@
 \epsscale{1}
-\caption{Upper Left:  SDSS image of Malin 2.
+\caption{Upper Left:  SDSS image of Malin~2.
 Upper Right:  Image made with the VIRUS-P datacube synthetic fiber magnitudes.
@@
 \plottwo{Plots/UGC06614bin_map.eps}{Plots/UGC06614binned_spec.eps}
-\caption{Left:  Map showing which fibers were binned for UGC 6614.
+\caption{Left:  Map showing which fibers were binned for UGC~6614.
 Right:  The binned spectra, color-coded to match the map on the left.
@@
 Also see \citet{Capp11} that says slow rotators are very rare in the field.
-So it might be strange if Malin 2 and UGC 6614 are slow rotators.
+So it might be strange if Malin~2 and UGC~6614 are slow rotators.
 

### 2016-08-07 glsb.tex
update Victor status and funding
changed affiliation + typo

@@
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{1}, Victor P. Debattista\altaffilmark{3}
+\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5}, Victor P. Debattista\altaffilmark{3}
   }
@@
 \altaffiltext{2}{University of Michigan}
-\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.  RCUK Fellow}
+\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
 \altaffiltext{4}{California Institute of Technology}
+\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
+(CEOU), Department of Physics \& Astronomy, Seoul
+National University, Seoul 151-742, Republic of Korea}
 
@@
 Observations of Malin~1 support the accretion model of GLSBs.
-\citet{Barth07} analyze HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging.
+\citet{Barth07} analyzes HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging.
 \citet{Barth07} points out that extended disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).
@@
 Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
-%Thanks to the observing specialists at Apache Point for their help executing our remote observations.
+
+VPD is supported by STFC Consolidated grant \#ST/M000877/1.
 

### 2016-11-17 glsb.tex

@@
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5}, Victor P. Debattista\altaffilmark{3}
+\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5,6}, Victor P. Debattista\altaffilmark{3}
   }
@@
 National University, Seoul 151-742, Republic of Korea}
+\altaffiltext{6}{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}
 

### 2016-11-22 final/ms.tex
make a submission version

--- 2016-11-17 glsb.tex
@@
-%\documentclass[12pt,preprint]{aastex}
-\documentclass{emulateapj}
+\documentclass[12pt,preprint]{aastex}
+%\documentclass{emulateapj}
 \usepackage{url}
@@
 We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.
-We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
+We argue that Malin~2 and UGC~6614 are normal elliptical galaxies that have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
 We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.
@@
 Observers tend to classify GLSB systems as normal spirals.
-\citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.
+\citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} conclude that GLSB systems are an extreme form of late type spiral galaxies.
 Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.
 Even the Galaxy Zoo project \citep{Willett13}  classifies GLSB galaxies as spirals.
-While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.
+While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest normal spirals \citep[Figure~4]{Dalcanton97}.
 
 The disks in GLSB systems are incredibly large, with Malin~1 being detected in $R$-band to a radius of over 100 kpc \citep{Moore06}.
-Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.
+Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation theories and more exotic formation scenarios have been proposed for GLSB systems.
 \citet{Mapelli08} form GLSB-like galaxies in simulations via the fading of collisional ring galaxies.
@@
 
-%These distances have occasionally been reached by x-ray observations of giant elliptical galaxies \citep{Buote12}.
-
-%In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.
-
-%The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.
-The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum.
--this goes in the discussion I think.
-\citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.
-
-%\citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
-Lots of good stuff on fast/slow rotators.
-Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.
-They don't see any sharp transition like I do, all very smooth age and metal curves.
-
 In one of the most extensive studies of a GLSB system, \citet{Kasparova14} combine ARC 3.5m photometry and long-slit spectra with Gemini spectra to mass-model Malin~2.
@@
 In \S\ref{sec:obs} we present new observations of Malin~2 and UGC~6614.
-In \S\ref{sec:compare_gals}, we compare the general properties of GLSB galaxies to sample of galaxies drawn from SDSS and the THINGS survey.
+In \S\ref{sec:compare_gals}, we compare the general properties of GLSB galaxies to samples of galaxies drawn from the Sloan Digital Sky Survey (SDSS) and  The \HI Nearby Galaxy Survey (THINGS).
 In \S\ref{sec:kinematics} and \S\ref{sec:sfh} we measure the stellar kinematics and star formation histories from our spectra.
@@
 
-%\citet{Pickering97} has the \HI\ rotation curves of these guys.
-For UGC~6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.
-And $3.6 \pm 0.4 \times 10^{10} \msun h_{75}^{-2}$for Malin~2.
-Notes that these are galaxies that are massive and DM dominated.
-In Malin~2, they find some gas moving relative to the regular rotating disk, and suspect that a dwarf fell though and stimulated star formation and this could be how stars managed to form in the low density environment.
-
-%Can we say that the stars formed in a higher density environment and then got dispersed.
-
-%\citet{Das13} look at the environments of GLSB systems.
-He says that GLSBs are an extreme form of late type spiral galaxies.
-I think I can show that no, they are really normal elliptical galaxies that happen to have accreted disks.
-
-%Nice paper on galaxies that live in voids and how one did manage to build a polar \HI\ disk with no stars: \citet{Stanonik09}
-
-%Chemical abundances in a polar disk:  \citet{Spavone10}
-
-%a near scoop by \citet{Lelli10}.
-They re-analyze \HI\ data on Malin 1 and one other.
-But a nice place to look for introduction material.
-They point out that GLSB galaxies might be normal HSB galaxies in the center.
-They claim to see steeply rising rotation curves, and compare to formation mechanisms.
-
-%\citet{Morganti97} look at an elliptical with an \HI\ disk.  Find a nice flat rotation curve.
-%\citet{Emonts08}  Another massive \HI\ ring around an S0 galaxy.
-%\citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.
-
-%\citet{Ibata05} look at extended disk of M31.
-%\citet{Ibata13} claim M31 satellites are co-planer.  
-%\citet{McConnachie09} M31 survey showing lots of merger structure.
-
-%Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html
-%another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm
-
-%From \citet{Matthews01b}, \HI\ measurements on the gals:
-%name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
-%F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
-%UGC~6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
-%\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.
-I'll need to compare my stellar kinematics to the \HI\ kinematics.
-
-%\cite{Rahman2007} has Spitzer observations of a few GLSB galaxies.
-
-%\citet{Das10} find CO in Malin~2.  Make some points about it being stable
-
-%\citet{Mapelli12} making ring galaxies from off center collisions.  
-%\citet{Mapelli08} look at if ring galaxies could evolve into GLSB systems.
-
-%\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.  
-%\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.  
-%\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.
-They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.
-
-%\citet{Schweizer89} Do a similar study with IC 2006, where they observe an \HI\ ring around the elliptical galaxy to get the total mass at large radii.  Looks like they get out to about 12.5 kpc.
-
-%\citet{Oosterloo07} HIPASS detection of \HI\ gas around 30 early-type galaxies.
-Most have regular disk or ring kinematics.
-Suggest these are ancient.
-They don't seem to have the resolution to do in-depth kinematics and DM halo stuff.
-
-%\citet{Magain13} look at strong lenses around 25 ellipticals, and then claim they see no evidence for extended DM halos.
-Confusing plot--Maybe they get out to 5 $R_{1/2}$?
-They say they only need a factor of 2, that could come from baryonic dark matter.
-
-%\citet{Spray95} CCD imaging of 8 GLSB systems.
-
-%\citet{Morganti13} Do modeling of ellipticals with declining velocity dispersion profiles.  Good place to start looking for the best way to model the long-slit data.
-
-%\citet{Buote12} review of dark matter in ellipticals from x-ray observations.
-
-%-need to look up some Thilker papers on extended UV disks, since these objects could be similar.
-From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).
-UGC 3642, GALEX shows a disk, and \HI\ is counter rotating.
-
-%\citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.
-They think the gas and star formation is coming from minor mergers or accretion.
-
-%\citet{Salim12} Finds 2 more GLSB type objects -- could be a sign that there are multiple routes to making GLSB systems.
-
-\begin{deluxetable*}{l l c c c c c c}
+\begin{deluxetable}{l l c c c c c c}
 %\tabletypesize{\small \footnotesize \scriptsize}
@@
 \tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
-\end{deluxetable*}
-
-% SDSS stellar masses.  using stellarMassFSPSGranEarlyDust:
-% Malin~2:  logMass	11.3307373297902
-% Malin 1:  logMass	11.1328074307929
-% UGC~6614: logMass	10.8745260407613
-
-% Updating the Pickering MI masses:
-% M_\HI\ = 2.36e5 * D^2 * int(S)
-% D = c(z+0.5(1.0-q_0)z^2)/H_0
-% int(S) = 4.4 Jy km/s for Malin~2
-%        = 15.0 for UGC~6614
-% cosmolopy using h = 0.704.  
-% cosmolopy says D_L = 202.9 and 90.9 Mpc
-% so that gives me M_\HI\'s of 4.27e10 and 2.92e10
-
-%  using scales of 0.940 and 0.444 kpc/arcsec.
+\end{deluxetable}
 
@@
 \end{deluxetable}
-
-%The other way to measure the dark matter halo of an elliptical is to use gravitational lensing.  \citet{Belokurov07} find a large ring in SDSS.
-
-%list of more lense papers here: http://www.galaxyzooforum.org/index.php?topic=275811.0
 
@@
 Flux standard stars were observed in twilight.
-
-%dates:  Feb 19, 20, 2010.  March 18-21, 2010.  April 6-8, 2010.
 
@@
 
-% Let's punt the APO spectra to the next paper--I don't think it adds much to this one anyway.
-%\subsection{Longslit spectra}
-
-%Observations were made using the Dual Imaging Spectrograph (DIS) on
-%the ARC 3.5 meter telescope at Apache Point Observatory (APO).
-Malin~2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.
-Both galaxies were observed with the  gratings and multiple positions of the 1.5\arcsec\ slit.
-%-insert table with galaxy name, position, total exposure time
-%-insert figure showing slit positions overlayed on the SDSS thumbnails.
-
 \section{Comparisons to Other Galaxies}\label{sec:compare_gals}
@@
 By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.
-In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC~6614.
+In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1, Malin 2, and UGC~6614.
 In this section, we compare the properties of the GLSB centers and disks with other systems.
@@
 
-% based on WMAP7+BAO+H0 mean
-%>>> fidcosmo
-%{'tau': 0.087, 'omega_n_0': 0.0, 'sigma_8': 0.809, 'h': 0.704, 'N_nu': 0, 'omega_lambda_0': 0.7274, 'n': 0.963, 'Y_He': 0.24, 'z_reion': 10.4, 'omega_b_0': 0.0456, 'omega_k_0': 0.0, 't_0': 13.75, 'omega_M_0': 0.2726}
-
 Figure~\ref{elliptical_relations} shows where the GLSBs fall on the major galaxy relations.
@@
 \epsscale{.4}
-\plotone{Plots/Color_Magnitu_Diagram.eps}\plotone{Plots/Faber_Jackson_Relation.eps}\\
-\plotone{Plots/Fundamental_Plane.eps}\plotone{Plots/mg_sigma.eps}
+\plotone{Color_Magnitu_Diagram.eps}\plotone{Faber_Jackson_Relation.eps}\\
+\plotone{Fundamental_Plane.eps}\plotone{mg_sigma.eps}
 \epsscale{1}
@@
 
-%For comparison, \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.
-
-%Papers that have large \HI\ rotation curves that I might compare to:
-%\citet{DeBlok2008,Swaters09,Verheijen01}
-
 The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 80 kpc \citep{Galaz15}.
@@
 
-% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
 \begin{figure*}
 \epsscale{.5}
-\plotone{Plots/things.eps}
+\plotone{things.eps}
 \epsscale{1}
@@
 \section{Kinematics}\label{sec:kinematics}
-
-%It would be nice to be able to use just the OII doublet to measure gas velocities from some of the galaxies.
-Paper that discusses the range of OII ratio values in \citet{Wang04}.
-Looks like it's usually around 0.5, but in low density regions it goes to 1.4.
-Fuck.
 
@@
 
-%using /astro/store/shared-scratch1/yoachim/Research/GLSB/Analysis/mass_estm.pro
 If we use the circular speed of the \HI\ data from the literature, we end up with dynamical masses of $25\times 10^{11} \msun$ for Malin~2 and $6.5\times 10^{11} \msun$ for UGC~6614 (dynamical to stellar mass ratios of 18 and 14 respectively).
-%Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.
-
-%$R_e = 7.3$\arcsec for UGC06614\\
-%$R_e = 7.17$\arcsec for Malin2
-
-%-crap, whatever happened to the gas kinematics?
-There are emission lines out there--are they bright enough to get in single fibers of not?
-Looks like for Malin~2 the emission lines are only coming from one side of the galaxy.
-UGC~6614 is mostly emission from the center.
-
-%print, rcmass(42.,280.)
-%print, rcmass(17.,200.)
-
-%scales=[0.940, 0.444] ;kpc/arcsec.  CMB frame from NED
-%re = [7.17, 7.3] ;effective radii in arcsec
-
-%-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.
 
@@
 
-Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.
+Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the single best fitting model.
 We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.
@@
 When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.
-This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as 10 M$_\sun$ yr$^{-1}$.)
+This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as a constant 10 M$_\sun$ yr$^{-1}$.)
 
@@
 In many cases, this eliminates nearly all fits except for the minimum.
-In these cases, we use the 4 best-fitting models to estimate the range of possible fits.
+In these cases, we use the 4 best-fitting models to estimate the range of possible parameters.
 
 The dominance of an old stellar population at large radii seems to contradict the star-burst formation mechanism of \citet{Mapelli08}, and favor an accretion model where a galaxy already containing old stars is disrupted by a massive elliptical galaxy similar to \citet{Pen06}.
-
-%\section{Disk Progenitors}
-
-%It should be relatively easy to speculate about the galaxies that merged to form the disk.
-I can pull \HI\ masses, and then calc some stellar masses given the SDSS photometry and my own stellar M/L ratios.
-Then given a baryonic mass and a typical stellar metallicity, it should be easy match that up to something.
-Using baryonic TF relation, I'm getting pretty large $V_c$ values for what the accreted galaxy would have been.
-I guess we could even speculate that this was a 3+ body encounter, so multiple gas rich systems that settle in.
-That would help explain the low metallicities.
-
-%Figure~\ref{thingsMHI} shows the total \HI\ mass for galaxies observed in the THINGS survey \citep{Walter2008}, along with the \HI\ masses for GLSB galaxies \citep{Pickering97}.
-
-%We can't really use the stellar luminosity of the disk to constrain the progenitor since there are signs of current {\emph in situ} star formation in the disks.
-However, the very low stellar metallicities point to low-mass progenitors.
-
-%Hard to estimate what the progenitor system of the disks were.
-Is there a good plot of disk \HI\ mass and metallicity out there?
-Might even need to measure Lick indices to try and get everything on the same metallicity system.
-
-%These systems are rare enough, that one might imagine rather complicated scenarios for creating them.
-For example, a three-body encounter could eject one galaxy while leaving a second in a nearly circular orbit.
-Back of the envelope, a galaxy ejected at 5000 \kms would go 1.5 degrees per gigayear.
-Even if the ejection was partly along the line of sight, it would be hard to find several gigayears later.
-Unlike the collisional ring scenario where one would expect the galaxy that stimulated the ring formation to still be nearby.
 
@@
 
-%--now on new mac.  /Users/yoachim/Research/GLSB/THINGS/guess_projen.py
 \begin{figure*}
 \epsscale{0.5}
-\plotone{Plots/things_projenguess.eps}
+\plotone{things_projenguess.eps}
 \epsscale{1}
@@
 Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7).
-We have also spatially binned data, possibly washing out how sharp the transition is between bulge and disk.
+We have also spatially binned data, possibly diluting how sharp the transition is between bulge and disk.
 
@@
 In their Figure~9, they combine the data to show a typical gas metallicity curve that drops linearly until $r_e\sim2$ and then flattens to a constant value.
-This shape is very different from the step function change we observe in the GLSBs.
+This shape is very different from the step function change we observe in GLSBs.
 
@@
 The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin~2 and $\sim -0.68$ for UGC~6614.
-These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
-Other cites for elliptical gradients \citep{Kuntschner10}
-
+These are very steep compared to gradients typically observed in elliptical galaxies \citep{Kuntschner10, Greene12, Greene15}.
 \citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.
 
-% Malin~2: R_e = 7.17"
-% UGC : 7.3"
-
 \citet{Kasparova14} present one of the most in depth observational studies of Malin~2.
-Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc.
+Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc best fits the dynamics.
 \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.
@@
 
-%Based on observations obtained with the Apache Point Observatory
-%3.5-meter telescope, which is owned and operated by the Astrophysical
-%Research Consortium.
-
 This research made use of the ``K-corrections calculator'' service available at http://kcor.sai.msu.ru/
@@
 
-%\bibliography{/astro/users/yoachim/Dropbox/Papers/Bib_files/big_jabref}
-%\bibliography{/Users/yoachim/Dropbox/Papers/Bib_files/big_jabref.bib}
-\bibliography{big_jabref.bib}
+\bibliography{ms}
 
 \begin{figure}
-\plottwo{Plots/sdssbinned_Malin2.eps}{Plots/Malin2mu.eps}
+\plottwo{sdssbinned_Malin2.eps}{Malin2mu.eps}
 \epsscale{.5}
-\plotone{Plots/Malin2profile_fit.eps}
+\plotone{Malin2profile_fit.eps}
 \epsscale{1}
@@
 
-%\begin{figure}
-%%\plottwo{Plots/Malin2stellarv.eps}{Plots/Malin2disp.eps}\\
-%%\epsscale{0.5}
-%\plottwo{Plots/Malin2stellarv.eps}{Plots/binned_Malin2svmap.eps}
-%%\epsscale{1}
-%\caption{Stellar kinematics.}
-%\end{figure}
-
-%\begin{figure}
-%\plottwo{Plots/sellarv_trimmed_malin2.eps}{Plots/rc_malin2.eps} \\
-%\plottwo{Plots/binned_stelv_trimmed_malin2.eps}{Plots/binned_rc_trimmed_malin2.eps}
-%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
-%\end{figure}
-%do an actual tilted ring fit to this shit.
-
 \begin{figure*}
 \epsscale{0.25}
-\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps} \\
-\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
+\plotone{dataMalin2.eps}\plotone{modelMalin2.eps}\plotone{data_modelMalin2.eps} \\
+\plotone{databinned_Malin2.eps}\plotone{modelbinned_Malin2.eps}\plotone{data_modelbinned_Malin2.eps}
 %\epsscale{.5}
 \epsscale{1}
-%\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
 \caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into triples.
 Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
-Middle:  Best fitting tilted ring model from kinemetry \citet{Krajn06}.
+Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}.
 Right: Best fit residuals.
@@
 \epsscale{0.25}
-%\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps} \\
-%\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
-%\epsscale{.5}
 \epsscale{1}
-\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
+\plottwo{kinembinned_Malin2.eps}{kinem_HI_binned_Malin2.eps}
 \caption{Rotation curves extracted from the best fitting models in Fig~\ref{malin_kinem_fibers}.
@@
 Vertical lines mark $R_e$ and $5R_e$.
-\HI\ data from \citet{Pickering97}.
+Right panel includes \HI\ data from \citet{Pickering97}.
 \label{malin_kinem}}
@@
 
-%\begin{figure}
-%\epsscale{0.25}
-%\plotone{Plots/oii_fluxMalin2.eps}\plotone{Plots/oiii_fluxMalin2.eps}\plotone{Plots/hbfluxMalin2.eps}
-%\plotone{Plots/oii_fluxbinned_Malin2.eps}\plotone{Plots/oiii_fluxbinned_Malin2.eps}\plotone{Plots/hbfluxbinned_Malin2.eps}
-%\epsscale{1}
-%\caption{Emission line maps.}
-%\end{figure}
-
 \begin{figure}
-\plottwo{Plots/Malin2bin_map.eps}{Plots/Malin2binned_spec.eps}
+\plottwo{Malin2bin_map.eps}{Malin2binned_spec.eps}
 \caption{Left:  Map of which fibers were binned together for star formation history measurements.
@@
 
-%\begin{figure}
-%\plottwo{Plots/rsfr_ebMalin2.eps}{Plots/rel_ebMalin2.eps}
-%\caption{The best fitting star formation histories and resulting total stellar masses.  \label{sfh_malin2}}
-%\end{figure}
-
-%\begin{figure}
-%\epsscale{.5}
-%\plotone{Plots/Malin2zgrad.eps}
-%\epsscale{1}
-%\caption{Stellar metallicity gradient. \label{metal_malin2}}
-%\end{figure}
-
 \begin{figure}
 \epsscale{.5}
-\plotone{Plots/Malin2_chibar_sfr.eps}
+\plotone{Malin2_chibar_sfr.eps}
 \epsscale{1}
@@
 \epsscale{.5}
-\plotone{Plots/Malin2_chibar_z.eps}
+\plotone{Malin2_chibar_z.eps}
 \epsscale{1}
@@
 \begin{figure}
-\plottwo{Plots/sdssbinned_UGC06614.eps}{Plots/UGC06614mu.eps}
+\plottwo{sdssbinned_UGC06614.eps}{UGC06614mu.eps}
 \epsscale{0.5}
-\plotone{Plots/UGC06614profile_fit.eps}
+\plotone{UGC06614profile_fit.eps}
 \epsscale{1}
@@
 
-%\begin{figure}
-%%\plottwo{Plots/UGC06614stellarv.eps}{Plots/UGC06614disp.eps}\\
-%%\epsscale{0.5}
-%\plottwo{Plots/UGC06614svmap.eps}{Plots/binned_UGC06614svmap.eps}
-%%\epsscale{1}
-%\caption{Stellar kinematics.}
-%\end{figure}
-
-%\begin{figure}
-%\plottwo{Plots/sellarv_trimmed_UGC06614.eps}{Plots/rc_UGC06614.eps}
-%\plottwo{Plots/binned_stelv_trimmed_binned_UGC06614.eps}{Plots/binned_rc_trimmed_binned_UGC06614.eps} \\
-%\caption{Fitted rotation curve after clipping outliers for the stellar velocity maps and the binned maps.}
-%\end{figure}
-
 \begin{figure}
-\plottwo{Plots/UGC06614bin_map.eps}{Plots/UGC06614binned_spec.eps}
+\plottwo{UGC06614bin_map.eps}{UGC06614binned_spec.eps}
 \caption{Left:  Map showing which fibers were binned for UGC~6614.
@@
 
-%\begin{figure}
-%\plottwo{Plots/rsfr_ebUGC06614.eps}{Plots/rel_ebUGC06614.eps}
-%\caption{The best fitting star formation histories and resulting total stellar mass fractions.
-For all radial bins, the stellar mass is dominated by stars older than 2 Gyr.
-Error bars represent the best fitting models.
-\label{sfh_ugc} }
-%\end{figure}
-
-%\begin{figure}
-%\epsscale{.5}
-%\plotone{Plots/UGC06614zgrad.eps}
-%\epsscale{1}
-%\caption{Stellar metallicity gradient.  \label{metal_ugc}}
-%\end{figure}
-
 \begin{figure}
 \epsscale{.5}
-\plotone{Plots/UGC06614_chibar_sfr.eps}
+\plotone{UGC06614_chibar_sfr.eps}
 \caption{Best fitting star formation histories.
@@
 \epsscale{.5}
-\plotone{Plots/UGC06614_chibar_z.eps}
+\plotone{UGC06614_chibar_z.eps}
 \epsscale{1}
@@
 \epsscale{0.25}
-\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps} \\
-\plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
+\plotone{dataUGC06614.eps}\plotone{modelUGC06614.eps}\plotone{data_modelUGC06614.eps} \\
+\plotone{databinned_UGC06614.eps}\plotone{modelbinned_UGC06614.eps}\plotone{data_modelbinned_UGC06614.eps}
 \epsscale{1}
@@
 Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
-Middle:  Best fitting tilted ring model from kinemetry \citet{Krajn06}.
+Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}.
 Right: Best fit residuals.
@@
 \epsscale{1}
-\plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
+\plottwo{kinembinned_UGC06614.eps}{kinem_HI_binned_UGC06614.eps}
 \caption{Rotation curves extracted from the best fitting model in Fig~\ref{ugc_kinem_fibers}.
@@
 Vertical lines mark $R_e$ and $5R_e$.
-\HI\ data from \citet{Pickering97}.
+Right panel includes \HI\ data from \citet{Pickering97}.
 \label{ugc_kinem}}
 \end{figure*}
-
-%\begin{figure}
-%\epsscale{0.25}
-%\plotone{Plots/oii_fluxUGC06614.eps}\plotone{Plots/oiii_fluxUGC06614.eps}\plotone{Plots/hbfluxUGC06614.eps}
-%\plotone{Plots/oii_fluxbinned_UGC06614.eps}\plotone{Plots/oiii_fluxbinned_UGC06614.eps}\plotone{Plots/hbfluxbinned_UGC06614.eps}
-%\epsscale{1}
-%\caption{Emission line maps.}
-%\end{figure}
-
-%\begin{figure}
-%\epsscale{.5}
-%\caption{ \emph{continued}.}
-%\end{figure}
 
@@
 
-Outline for discussion section
-\begin{itemize}
-\item{We find the GLSB systems Malin~2 and UGC~6614 are observationally most consistent with being normal elliptical galaxies that have undergone a high angular momentum minor merger with a gas rich system.}
-\item{recap photometric evidence--the centers look just like SDSS ellipticals.}
-\item{recap star formation histories. Disk is dominated by old stars.}
-\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.
-      \citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.
-Lots of good stuff on fast/slow rotators.
-Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.
-They don't see any sharp transition like I do, all very smooth age and metal curves.
-}
-\item{extended comparison to \citet{Kasparova14}}
-  \begin{itemize}
-    \item{Mass model of Malin~2 requires a huge isothermal core radius.}
-    \item{They measure gas metallicities and find solar in the center and half-solar at 20-30 kpc.
-While it is a fool's errand to compare metallicities between stars and gas, it is interesting that the gas metallicity gradient is much smaller than in the stars.
-If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.
-Hmm, looking at DR12 stuff, the pipeline reductions are fitting solar metallicity to the center, not sure I believe that.
-}
-      \item{They have a nice mass-model that becomes dark matter dominated at around r=20 kpc.  Could this be the normal shape of elliptical dark matter halos?}
-  \end{itemize}
-
-\item{This could be the strongest evidence for very massive elliptical dark matter halos. }
-  \item{plan on getting higher spatial resolution spectra of the centers to confirm they are typical elliptical galaxies.}
-\end{itemize}
-
-Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.
-Also see \citet{Capp11} that says slow rotators are very rare in the field.
-So it might be strange if Malin~2 and UGC~6614 are slow rotators.
-
 % LocalWords:  Debattista Horrocks Lancashire RCUK Malin Stanonik Spavone Lelli

### 2016-11-22 final/copy_plots.sh
scripts

@@ -1,0 +1,37 @@
+cp ../Plots/Color_Magnitu_Diagram.eps .
+cp ../Plots/Faber_Jackson_Relation.eps .
+cp ../Plots/Fundamental_Plane.eps .
+cp ../Plots/mg_sigma.eps .
+cp ../Plots/things.eps .
+cp ../Plots/things_projenguess.eps .
+cp ../Plots/sdssbinned_Malin2.eps .
+cp ../Plots/Malin2mu.eps .
+cp ../Plots/dataMalin2.eps .
+cp ../Plots/modelMalin2.eps .
+cp ../Plots/data_modelMalin2.eps .
+cp ../Plots/databinned_Malin2.eps .
+cp ../Plots/modelbinned_Malin2.eps .
+cp ../Plots/data_modelbinned_Malin2.eps .
+cp ../Plots/kinembinned_Malin2.eps .
+cp ../Plots/kinem_HI_binned_Malin2.eps .
+cp ../Plots/Malin2bin_map.eps .
+cp ../Plots/Malin2binned_spec.eps .
+cp ../Plots/Malin2_chibar_sfr.eps .
+cp ../Plots/Malin2_chibar_z.eps .
+cp ../Plots/sdssbinned_UGC06614.eps .
+cp ../Plots/UGC06614mu.eps .
+cp ../Plots/UGC06614bin_map.eps .
+cp ../Plots/UGC06614binned_spec.eps .
+cp ../Plots/UGC06614_chibar_sfr.eps .
+cp ../Plots/UGC06614_chibar_z.eps .
+cp ../Plots/dataUGC06614.eps .
+cp ../Plots/modelUGC06614.eps .
+cp ../Plots/data_modelUGC06614.eps .
+cp ../Plots/databinned_UGC06614.eps .
+cp ../Plots/modelbinned_UGC06614.eps .
+cp ../Plots/data_modelbinned_UGC06614.eps .
+cp ../Plots/kinembinned_UGC06614.eps .
+cp ../Plots/kinem_HI_binned_UGC06614.eps .
+ cp ../Plots/Malin2profile_fit.eps .
+ cp ../Plots/UGC06614profile_fit.eps .
+ 

### 2016-11-22 final/maketar.sh

@@ -1,0 +1,1 @@
+tar -cvzf ms.tar.gz ms.tex ms.bib *.eps

### 2017-01-24 final/ms.tex
put sentences on own lines
remove 'normal'

@@
 \begin{abstract}
-We present IFU observations of the giant low surface brightness galaxies Malin~2 and UGC~6614.
+We present IFS observations of the giant low surface brightness galaxies Malin~2 and UGC~6614.
 We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.
-We argue that Malin~2 and UGC~6614 are normal elliptical galaxies that have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
+We argue that Malin~2 and UGC~6614 are early-type elliptical galaxies that have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.
 We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.
@@
 
-Observers tend to classify GLSB systems as normal spirals.
+Observers tend to classify GLSB systems as late-type spirals.
 \citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} conclude that GLSB systems are an extreme form of late type spiral galaxies.
@@
 Even the Galaxy Zoo project \citep{Willett13}  classifies GLSB galaxies as spirals.
-While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest normal spirals \citep[Figure~4]{Dalcanton97}.
+While GLSB systems superficially resemble late-type spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest spirals \citep[Figure~4]{Dalcanton97}.
 
@@
 
-The other popular formation scenario for GLSB systems is that they are normal galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
+The other popular formation scenario for GLSB systems is that they are galaxies that undergo a high angular momentum minor merger where the LSB disk is the shredded remains of an accreted galaxy.
 \citet{Pen06} find that extended disks can be formed via the disruption of dwarf galaxies.
@@
 Observations of Malin~1 support the accretion model of GLSBs.
-\citet{Barth07} analyzes HST imaging of Malin~1 and find that the central object is well described as a normal early-type barred galaxy that was previously unresolved in ground-based imaging.
+\citet{Barth07} analyzes HST imaging of Malin~1 and find that the central object is well described as an early-type barred galaxy that was previously unresolved in ground-based imaging.
 \citet{Barth07} points out that extended disk structures in galaxies such as M31 appear to be a smooth continuation of the inner disk \citep{Ferguson02}, while Malin~1's extended disk is better described as a distinct component, (although \citet{Ibata05} claim M31's extended disk is of accretion origin).
@@
 \enddata
-\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
+\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.
+The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
 \end{deluxetable}
@@
 
-We obtained spatially resolved spectroscopy of our target galaxies using the Mitchell Spectrograph (formerly VIRUS-P)\citep{Hill08} on the 2.7m Harlan J.
-Smith telescope at McDonald Observatory.
+We obtained spatially resolved spectroscopy of our target galaxies using the Mitchell Spectrograph (formerly VIRUS-P)\citep{Hill08} on the 2.7m Harlan J. Smith telescope at McDonald Observatory.
 Observations were made during dark time in February, March, and April 2010.
 Identical instrument setups were used for all observations.
-The Mitchell Spectrograph with the VP-2 IFU bundle used here has a square array of 246 optical fibers which sample the 1.9\arcmin$\times$1.9\arcmin\ field-of-view with a 1/3 filling factor, with each fiber having a diameter of 4.23\arcsec.
+The Mitchell Spectrograph with the VP-2 IFS (Integral Field Spectrograph) bundle used here has a square array of 246 optical fibers which sample the 1.9\arcmin$\times$1.9\arcmin\ field-of-view with a 1/3 filling factor, with each fiber having a diameter of 4.23\arcsec.
 The spectrograph images the spectrum of each fiber on a 2048$\times$2048 Fairchild Imaging CCD.
@@
 We use the b-spline procedure described in \citet{Kelson03} to generate background frames.
-The corners of the IFU array contain enough empty fibers to measure the sky background in each exposure.
+The corners of the IFS array contain enough empty fibers to measure the sky background in each exposure.
 Because we bin fibers together, imperfect sky-subtraction represents a serious source of potential systematic errors.
@@
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
-From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively normal red elliptical galaxies.
+ From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively red elliptical galaxies on the red-sequence.
 \label{elliptical_relations}}
@@
 
-We follow \citet{Bernardi03,Bernardi03b} in fitting fundamental plane parameters to our selected SDSS galaxies.  We fit the fundamental plane by minimizing $\chi^2$ in, 
+We follow \citet{Bernardi03,Bernardi03b} in fitting fundamental plane parameters to our selected SDSS galaxies.
+We fit the fundamental plane by minimizing $\chi^2$ in, 
 \begin{equation}
@@
 While the stellar disk of UGC~6614 is close in size to local observed \HI\ disks, Malin~1 and~2 are larger than the \HI\ disks observed in the THINGS survey.
-This seems to point against the GLSB formation mechanism of \citet{Mapelli08}, as we do not observe \HI\ disks in normal spirals large enough to convert into GLSB systems unless an interaction is able to also boost the angular momentum of the resulting stellar disk.
+This seems to point against the GLSB formation mechanism of \citet{Mapelli08}, as we do not observe \HI\ disks in late-type spirals large enough to convert into GLSB systems unless an interaction is able to also boost the angular momentum of the resulting stellar disk.
 
@@
 
-As we have shown in \S\ref{sec:centers} and \S\ref{sec:disks}, GLSB galaxies can be well described as large normal ellipticals that have managed to accrete a high angular momentum disk of stars and gas.
+As we have shown in \S\ref{sec:centers} and \S\ref{sec:disks}, GLSB galaxies can be well described as massive early-type galaxies that have managed to accrete a high angular momentum disk of stars and gas.
 Given the total \HI\ mass in GLSBs, the accreted object is consistent with a much lower-mass gas-rich spiral.
@@
 
-\citet{Murphy2011} are able to use IFU observations of M87 to reach $\sim2 R_e$ using just stellar data, and then rely on globular cluster kinematics to extended out to $5 R_e$ where they find a dark matter fraction of 85\%.
-\citet{Weij09} is similarly able to use IFU observations to reach $\sim 4 R_e$ on two elliptical galaxies while \citet{Proctor09} reaches $\sim 3 R_e$ using multi-object spectroscopy.
+\citet{Murphy2011} are able to use IFS observations of M87 to reach $\sim2 R_e$ using just stellar data, and then rely on globular cluster kinematics to extended out to $5 R_e$ where they find a dark matter fraction of 85\%.
+\citet{Weij09} is similarly able to use IFS observations to reach $\sim 4 R_e$ on two elliptical galaxies while \citet{Proctor09} reaches $\sim 3 R_e$ using multi-object spectroscopy.
 
@@
 We do not include any metallicity evolution, as all the age bins in a given model have the same metallicity.
-This gives us 361 unique non-zero model spectra.
-We use \citet{Bruzual03} with a Chabrier IMF to generate the model spectra.
+This gives us 361 unique non-zero model spectra. We use \citet{Bruzual03} with a Chabrier IMF to generate the model spectra.
 
@@
 
-We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin~1 \citep{Barth07} and NGC~7589 \citep{Lelli10}.
+We find that the centers of these two GLSB systems very closely resemble typical early-type galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin~1 \citep{Barth07} and NGC~7589 \citep{Lelli10}.
 
@@
 
-It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.
+It also seems unlikely that GLSBs are just extreme versions of late-type disk galaxies \citep{Das13}.
 It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.
@@
 For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.
-This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.
+This is a very sharp gradient compared to what has been found in late-type spirals for the bulge-to-disk transition region.
 \citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.
@@
 
-We have observed two giant low surface brightness galaxies with the VIRUS-P IFU.
+We have observed two giant low surface brightness galaxies with the VIRUS-P IFS.
 We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a large disk.
@@
 
-We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are normal elliptical galaxies and constrain a more sophisticated dynamical model of the system.
+We are currently observing higher spatial resolution IFS data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confirm they are typical early-type galaxies and constrain a more sophisticated dynamical model of the system.
 
@@
 Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
+Thanks to the anonymous referee for a very thorough and prompt report which improved the paper.
 
@@
 \caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into triples.
-Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
-Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}.
-Right: Best fit residuals.
+Left:  Stellar velocities measured with pPXF \citep{Cappellari04}. Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}. Right: Best fit residuals.
 \label{malin_kinem_fibers}}
@@
 Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
-The inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines.
-\label{malin2_binmap}}
+The inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines. \label{malin2_binmap}}
 \end{figure}
@@
 Right:  The binned spectra, color-coded to match the map on the left.
-As with Malin~2, the inner spectra show strong metallicity absorption features while the outer spectra show emission lines.
-\label{ugc_binmap}}
+As with Malin~2, the inner spectra show strong metallicity absorption features while the outer spectra show emission lines. \label{ugc_binmap}}
 \end{figure}
@@
 \epsscale{1}
-\caption{Best fitting stellar metallicities for the binned UGC~6614 spectra.  Dashed line shows the maximum model value.  \label{metal_ugc}}
+\caption{Best fitting stellar metallicities for the binned UGC~6614 spectra.
+Dashed line shows the maximum model value.
+\label{metal_ugc}}
 \end{figure}
@@
 \caption{Upper panels show kinematics from individual fibers, lower panels show the results after fibers have been binned into triples.
-Left:  Stellar velocities measured with pPXF \citep{Cappellari04}.
-Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}.
-Right: Best fit residuals.
+Left:  Stellar velocities measured with pPXF \citep{Cappellari04}. Middle:  Best fitting tilted ring model from kinemetry \citep{Krajn06}. Right: Best fit residuals.
 \label{ugc_kinem_fibers}}
@@
 Vertical lines mark $R_e$ and $5R_e$.
-Right panel includes \HI\ data from \citet{Pickering97}.
-\label{ugc_kinem}}
+Right panel includes \HI\ data from \citet{Pickering97}. \label{ugc_kinem}}
 \end{figure*}
@@
 % LocalWords:  SEDs Brookhaven Instituto Astrofisica Canarias Notre JINA DM
-% LocalWords:  IFU UGC HSB SAURON ellipticals Spitzer IC Galaz Myr
+% LocalWords:  IFS UGC HSB SAURON ellipticals Spitzer IC Galaz Myr
 % LocalWords:  kpc HIPASS CCD metallicity MANGA SDSS arcsec lensing IRAF

### 2017-01-24 final/ms.tex
merge plots

@@
 Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
-UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
+UGC 6614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
 \enddata
@@
 Malin~2 & 6.1 & 35.5  \\
-UGC 06614 & 5.7 & 33.4
+UGC 6614 & 5.7 & 33.4
 \enddata
@@
 Malin~2 had 10 exposures per dither position (11 exposures for dither position 1), for a total of 15 hours of exposure time.
-Observations of UGC 06614 had alignment issues between observing runs.
+Observations of UGC 6614 had alignment issues between observing runs.
 This resulted in a deep stack of 6 exposures, and a shallow stack with only 2 exposures.
@@
 In addition to individual fibers, we have binned sets of three neighboring fibers together to boost the signal-to-noise ratio and run pPXF on these super-fibers.
-The fiber surface brightnesses are plotted in Figures~\ref{Malin2_fibers} and~\ref{ugc_fibers}, and the pPXF stellar velocity maps are shown in Figures~\ref{malin_kinem} and~\ref{ugc_kinem}.
+The fiber surface brightnesses are plotted in Figure~\ref{galaxy_fibers}, and the pPXF stellar velocity maps are shown in Figure~\ref{gal_kinem}.
 
@@
 For these fits, we hold the position angle and inclination fixed to values found from fitting the fiber-photometry.
-Figures~\ref{malin_kinem} and~\ref{ugc_kinem} show the kinemetry fits and extracted rotation curves.
+Figure~\ref{gal_kinem} show the kinemetry fits and extracted rotation curves.
 We iterate the fit, clipping residuals which deviate from the model by more than 250 \kms.
@@
 
-The Malin~2 rotation curve (Figure~\ref{malin_kinem}) is rather complicated, having several abrupt rises.
+The Malin~2 rotation curve (Figure~\ref{gal_kinem}) is rather complicated, having several abrupt rises.
 This is especially strange given the very smooth photometric profile.
-UGC~6614 (Figure~\ref{ugc_kinem}), on the other hand, has a typical late-type galaxy rotation curve with a linear rise and flat outer region.
+UGC~6614, on the other hand, has a typical late-type galaxy rotation curve with a linear rise and flat outer region.
 One important difference is that the linear rise extends for 10 kpc.
@@
 
-Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin~2 and UGC 06614.
+Figure~\ref{gal_binmap} shows the fibers that were binned and the resulting spectra for Malin~2 and UGC 6614.
 Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.
@@
 
-The best fitting star formation histories are shown in Figures~\ref{sfh_malin2} and~\ref{sfh_ugc}, while the best fitting stellar metallicities are shown in Figures~\ref{metal_malin2} and~\ref{metal_ugc}.
+The best fitting star formation histories are shown in Figure~\ref{sfh_gals}, while the best fitting stellar metallicities are shown in Figure~\ref{metal_gals} .
 We find that {\emph{both galaxies have stellar populations dominated by old stars at all radii}}.
@@
 
-One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).
+One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figure~\ref{metal_gals}).
 For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.
@@
 \begin{figure}
-\plottwo{sdssbinned_Malin2.eps}{Malin2mu.eps}
-\epsscale{.5}
-\plotone{Malin2profile_fit.eps}
+\epsscale{.33}
+\plotone{sdssbinned_Malin2.eps}\plotone{Malin2mu.eps}\plotone{Malin2profile_fit.eps}
+\plotone{sdssbinned_UGC06614.eps}\plotone{UGC06614mu.eps}\plotone{UGC06614profile_fit.eps}
 \epsscale{1}
-\caption{Upper Left:  SDSS image of Malin~2.
-Upper Right:  Image made with the VIRUS-P datacube synthetic fiber magnitudes.
-Lower:  An exponential fit to the fiber magnitudes.
-Red points show fibers that were clipped while the solid line shows the best-fit.
-\label{Malin2_fibers} }
+\caption{Left:  SDSS images of Malin~2 and UGC 6614.
+Middle:  Images made with the VIRUS-P datacube synthetic fiber magnitudes.
+Right:  Exponential fits to the fiber magnitudes.
+Red points show fibers that were clipped while the solid lines show the best-fits.
+\label{galaxy_fibers} }
 \end{figure}
@@
 \epsscale{0.25}
-\epsscale{1}
-\plottwo{kinembinned_Malin2.eps}{kinem_HI_binned_Malin2.eps}
-\caption{Rotation curves extracted from the best fitting models in Fig~\ref{malin_kinem_fibers}.
-The dashed curves show the expected stellar mass contribution to the rotation curve.
-Vertical lines mark $R_e$ and $5R_e$.
-Right panel includes \HI\ data from \citet{Pickering97}.
-\label{malin_kinem}}
-\end{figure*}
-
-\begin{figure}
-\plottwo{Malin2bin_map.eps}{Malin2binned_spec.eps}
-\caption{Left:  Map of which fibers were binned together for star formation history measurements.
-Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
-The inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines. \label{malin2_binmap}}
-\end{figure}
-
-\begin{figure}
-\epsscale{.5}
-\plotone{Malin2_chibar_sfr.eps}
-\epsscale{1}
-\caption{ Best fitting star formation histories.
-For each bin, the SFH is normalized by the peak at each radius.
-Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.
-The oldest age bin dominates at all radii.
-\label{sfh_malin2} }
-\end{figure}
-
-\begin{figure}
-\epsscale{.5}
-\plotone{Malin2_chibar_z.eps}
-\epsscale{1}
-\caption{Best fitting stellar metallicities.
- Dashed line shows the maximum model metallicity used in the models (minimum is below the y range limit).
-Error bars are as in Figure~\ref{sfh_malin2}.
-\label{metal_malin2}}
-\end{figure}
-
-\begin{figure}
-\plottwo{sdssbinned_UGC06614.eps}{UGC06614mu.eps}
-\epsscale{0.5}
-\plotone{UGC06614profile_fit.eps}
-\epsscale{1}
-\caption{Upper Left:  SDSS image of UGC 06614.
-Upper Right:  Image made with the VIRUS-P datacube.
-Lower:  An exponential fit to the fiber magnitudes.
-Red points show fibers that were clipped while the solid line shows the best-fit.
-We only included fibers beyond the outer ring structure.
-\label{ugc_fibers} }
-\end{figure}
-
-\begin{figure}
-\plottwo{UGC06614bin_map.eps}{UGC06614binned_spec.eps}
-\caption{Left:  Map showing which fibers were binned for UGC~6614.
-Right:  The binned spectra, color-coded to match the map on the left.
-As with Malin~2, the inner spectra show strong metallicity absorption features while the outer spectra show emission lines. \label{ugc_binmap}}
-\end{figure}
-
-\begin{figure}
-\epsscale{.5}
-\plotone{UGC06614_chibar_sfr.eps}
-\caption{Best fitting star formation histories.
-For each bin, the SFH is normalized by the peak bin.
-Error bars are based on $\Delta\chi^2=100$ or the 4 best fitting models, whichever provides more points.
-As with Malin~2, old stars dominate at all radii.
-\label{sfh_ugc} }
-\epsscale{1}
-\end{figure}
-
-\begin{figure}
-\epsscale{.5}
-\plotone{UGC06614_chibar_z.eps}
-\epsscale{1}
-\caption{Best fitting stellar metallicities for the binned UGC~6614 spectra.
-Dashed line shows the maximum model value.
-\label{metal_ugc}}
-\end{figure}
-
-\begin{figure*}
-\epsscale{0.25}
 \plotone{dataUGC06614.eps}\plotone{modelUGC06614.eps}\plotone{data_modelUGC06614.eps} \\
@@
 \epsscale{1}
+\plottwo{kinembinned_Malin2.eps}{kinem_HI_binned_Malin2.eps}
 \plottwo{kinembinned_UGC06614.eps}{kinem_HI_binned_UGC06614.eps}
-\caption{Rotation curves extracted from the best fitting model in Fig~\ref{ugc_kinem_fibers}.
-The dashed curve shows the expected stellar mass contribution to the rotation curve.
+\caption{Rotation curves extracted from the best fitting models in Figures~\ref{malin_kinem_fibers} and~\ref{ugc_kinem_fibers}.
+The dashed curves show the expected stellar mass contribution to the rotation curve.
 Vertical lines mark $R_e$ and $5R_e$.
-Right panel includes \HI\ data from \citet{Pickering97}. \label{ugc_kinem}}
+Right panel includes \HI\ data from \citet{Pickering97}.
+\label{gal_kinem}}
 \end{figure*}
+
+\begin{figure}
+\plottwo{Malin2bin_map.eps}{Malin2binned_spec.eps}
+\plottwo{UGC06614bin_map.eps}{UGC06614binned_spec.eps}
+\caption{Left:  Maps of which fibers were binned together for star formation history measurements.
+Right:  Resulting binned spectra, residuals from the bright skyline at 5577\AA\ have been masked.
+For both galaxies, the inner bins show strong Mg, Fe, and Ca absorption features, while the outer bins have \hb\ and \ion{O}{3} emission lines. \label{gal_binmap}}
+\end{figure}
+
+\begin{figure}
+\plottwo{Malin2_chibar_sfr.eps}{UGC06614_chibar_sfr.eps}
+\caption{ Best fitting star formation histories.
+For each bin, the SFH is normalized by the peak at each radius.
+Error bars are based on $\Delta\chi^2=100$ or the best fitting 4 models, whichever provides more points.
+The oldest age bin dominates at all radii.
+\label{sfh_gals} }
+\end{figure}
+
+\begin{figure}
+\plottwo{Malin2_chibar_z.eps}{UGC06614_chibar_z.eps}
+\caption{Best fitting stellar metallicities.
+ Dashed line shows the maximum model metallicity used in the models (minimum is below the y range limit).
+Error bars are as in Figure~\ref{sfh_gals}.
+\label{metal_gals}}
+\end{figure}
 

### 2017-01-25 final/ms.tex
use non-default contour levels

@@
 \startdata
-Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
+Malin~1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
 Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
@@
 \tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.
-The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
+Redshift and photometric measurements from SDSS. Stellar masses calculated from \citet{Conroy09}}
 \end{deluxetable}
@@
 
-With our final reduced data cubes, we used Penalized Pixel-Fitting (pPXF) \citep{Cappellari04} and Gas AND Absorption Line Fitting (GANDALF) \citep{Sarzi06} on each fiber to fit stellar velocities, stellar dispersions, and emission line velocities and fluxes.
+With our final reduced data cubes, we used Penalized Pixel-Fitting (pPXF) \citep{Cappellari04} on each fiber to fit stellar velocities, stellar dispersions, and emission line velocities and fluxes.
 For stellar templates we use a suite of SSP spectra from \citet{Bruzual03}.
-We use GANDALF to measure the [\ion{O}{2}] doublet, [\ion{O}{3}] doublet, and the higher order Balmer lines \hb, H$\gamma$, H$\delta$, H$\epsilon$ while masking the night skyline at 5577 \AA.
-The fit also includes a 4th degree multiplicative polynomial to correct for any dust or flux calibration mis-match between the observations and templates.
-Because our data do not extend out to \ha, we cannot use the Balmer decrement to place tight constraints on the dust extinction.
 While pPXF fits the stellar velocity dispersion, our instrumental resolution is low enough ($\sim140$ \kms) that we are unable to make meaningful velocity dispersion measurements beyond the central fibers.
@@
 By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.
-In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1, Malin 2, and UGC~6614.
+In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin~1, Malin~2, and UGC~6614.
 In this section, we compare the properties of the GLSB centers and disks with other systems.
+In Table~\ref{basic_prop}, we list the basic properties of out target GLSB systems.
+Table~\ref{basic_prop} includes stellar masses for the systems XXX--add discussion of where those stellar masses come from.
+Need to figure out which version of FSPS model I actually copied.
+%http://skyserver.sdss.org/dr10/en/help/browser/browser.aspx?cmd=description+stellarMassFSPSGranEarlyDust+U#&&history=description+stellarMassFSPSGranEarlyDust+U
+%
 
@@
 The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them. 
+XXX-looks like the blue arm in Malin~2 gets shredded into a few dozen objects, as does the ring in UGC~6614.
+
+\citet{Bakos12} find that standard SDSS imaging reaches a S/N$\sim1$ per pixel at a surface brightness of 25 mag arcsec$^{-2}$, brighter than most GLSB disk components.
 
@@
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
+Contours are drawn which enclose 5\% to 85\% of the data with 20\% steps.
  From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively red elliptical galaxies on the red-sequence.
@@
 For these fits, we hold the position angle and inclination fixed to values found from fitting the fiber-photometry.
+Our fiber-photometry fits are listed in Table~\ref{fitted_params}. XXX--add more details to what I did here.
 Figure~\ref{gal_kinem} show the kinemetry fits and extracted rotation curves.
@@
 Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc best fits the dynamics.
+XXX--address how our new interpretation of the formation of the system as a merger remnant could help solve the discrepancy with that huge isothermal core. 
+XXX--rather than being an outlier late-type disk, they are probing the outskirts of an early-type galaxy, where wonky dark matter profiles are common xxx-cite Amy's paper, etc.
 \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.
@@
 
-We have observed two giant low surface brightness galaxies with the VIRUS-P IFS.
+We have observed two giant low surface brightness galaxies with the Mitchell Spectrograph IFS.
 We find the systems are best explained as massive elliptical galaxies which have managed to accrete stars and gas into a large disk.
@@
 Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
-Thanks to the anonymous referee for a very thorough and prompt report which improved the paper.
+We thank the anonymous referee for a very thorough and amazingly prompt report which improved the paper.
 
@@
 \caption{Left:  SDSS images of Malin~2 and UGC 6614.
-Middle:  Images made with the VIRUS-P datacube synthetic fiber magnitudes.
+Middle:  Images made with the Mitchell Spectrograph datacube synthetic fiber magnitudes.
 Right:  Exponential fits to the fiber magnitudes.

### 2017-01-26 final/ms.tex
minor tweaks

@@
 Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.
-Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.
+Bottom Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line. 
+UGC~6614 is a slight outlier, but still within the 85\% contour.
 Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
+Malin~1 is appears to be a metal-rich outlier. 
 Contours are drawn which enclose 5\% to 85\% of the data with 20\% steps.

### 2018-05-04 glsb.tex
cool new sim citation

@@
 In many cases, this eliminates nearly all fits except for the minimum.
-In these cases, we use the 4 best-fitting models to estimate the range of possible fits.
+In these cases, we use the 4 best-fitting models to estimate the range of possible parameters.
 
@@
 The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin~2 and $\sim -0.68$ for UGC~6614.
-These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.
-Other cites for elliptical gradients \citep{Kuntschner10}
+These are very steep compared to gradients typically observed in elliptical galaxies \citep{Kuntschner10, Greene12, Greene15}.
+\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.
 
-\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.
+XXX-While metallicity gradients this steep have not been observed, they do appear in simulations.
+\citet{Sanderson17} find that for their simulated Milky Way mass galaxies that a sharp break in stellar metallicity corresponds to the galactic radius where stellar populations become dominated by accretion.
+XXX--Should take a stab at saying how large the jump is.
 
@@
 \citet{Kasparova14} present one of the most in depth observational studies of Malin~2.
-Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc.
+Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc best fits the dynamics.
 \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.
@@
 Vertical lines mark $R_e$ and $5R_e$.
-\HI\ data from \citet{Pickering97}.
+Right panel includes \HI\ data from \citet{Pickering97}.
 \label{ugc_kinem}}

### 2018-05-16 glsb.tex
updated to aastex

@@
+\documentclass[12pt]{aastex62}
 %\documentclass[12pt,preprint]{aastex}
-\documentclass{emulateapj}
+%\documentclass{emulateapj}
 \usepackage{url}
@@
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5,6}, Victor P. Debattista\altaffilmark{3}
-  }
+\correspondingauthor{Peter Yoachim}
+\email{yoachim@uw.edu}
 
-\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
+\author[0000-0003-2874-6464]{Peter Yoachim}
+\altaffiliation{Department of Astronomy, \\
+University of Washington, Box 351580,\\
 Seattle WA, 98195}
-\altaffiltext{2}{University of Michigan}
-\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
-\altaffiltext{4}{California Institute of Technology}
-\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
-(CEOU), Department of Physics \& Astronomy, Seoul
+
+\author{Denise Schmitz}
+\altaffiliation{California Institute of Technology}
+
+\author{Sarah Loebman}
+\altaffiliation{University of Michigan}
+
+\author{SungWon Kwak}
+\altaffiliation{Center for the Exploration of the Origin of the Universe (CEOU),\\
+ Department of Physics \& Astronomy, Seoul\\
 National University, Seoul 151-742, Republic of Korea}
-\altaffiltext{6}{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}
+\altaffiliation{Korea Astronomy and Space Science Institute, \\
+Daejeon 305-348, Republic of Korea},
+
+\author{Victor P. Debattista}
+\altaffiliation{Jeremiah Horrocks Institute, \\
+University of Central Lancashire, Preston PR1 2HE, UK.}
 

### 2020-10-09 second_submission/ms.tex
getting to work

--- 2017-01-26 final/ms.tex
@@
 \def\arcsec{$^{\prime\prime}$}
-\bibliographystyle{apj}
+\bibliographystyle{aasjournal}
 \newcommand\degree{{^\circ}}
@@
 
-\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5,6}, Victor P. Debattista\altaffilmark{3}
+\author{Peter Yoachim\altaffiliation{Department of Astronomy, University of Washington, Box 351580,
+Seattle WA, 98195}, Denise Schmitz\altaffiliation{California Institute of Technology}, Sarah Loebman\altaffiliation{}, SungWon Kwak\altaffiliation{Center for the Exploration of the Origin of the Universe
+(CEOU), Department of Physics \& Astronomy, Seoul
+National University, Seoul 151-742, Republic of Korea}altaffilmark{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}, Victor P.
+Debattista\altaffiliation{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
   }
-
-\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
-Seattle WA, 98195}
-\altaffiltext{2}{University of Michigan}
-\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
-\altaffiltext{4}{California Institute of Technology}
-\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
-(CEOU), Department of Physics \& Astronomy, Seoul
-National University, Seoul 151-742, Republic of Korea}
-\altaffiltext{6}{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}
 
